---
format:
  docx: 
    reference-doc: "./bib/template.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
crossref:  
  fig-title: Fig.    # (default is "Figure")
  tbl-title: Table   # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.   # (default is "Table")
editor_options: 
  chunk_output_type: console
---

# Results

```{r}
#| label: load_packages
#| output: false
#| warning: false

    source("./R/func.R")
    pacman::p_load(tidyverse, brms, glmmTMB, gt, posterior)
    options(digits = 3)
```

```{r}
#| label: load_data
#| output: false
#| warning: false

############################
# Import processed data
#############################
  all_data <- read.table("./output/all_data_p.csv",header=T, sep=",")
  all_data

  
############################
# Parasite count
#############################
### Blackspots distribution
  hist(all_data$BS_post_tot)

# Blackspots info
  BS_min<-min(all_data$BS_post_tot)
  BS_max<-max(all_data$BS_post_tot)
  BS_median<-median(all_data$BS_post_tot)

### Cestodes distribution
  hist(all_data$P04_alive)

# Cestodes info
  cestode_min<-min(all_data$P04_alive)
  cestode_max<-max(all_data$P04_alive)
  cestode_median<-median(all_data$P04_alive)
  mean(all_data$P04_alive)

### Nematodes distribution
  hist(all_data$P013_alive)

# Nematodes info
  nematode_min<-min(all_data$P013_alive)
  nematode_max<-max(all_data$P013_alive)

### Looking at BS gained after infection
# Create new columns in the dataset
  all_data$BS_gain<- all_data$BS_post_tot - all_data$BS_pre

# BS gain distribution
  hist(all_data$BS_gain)

# BS gain info
  gain_min<-min(all_data$BS_gain) ### miscount, some fish have less BS after infection
  gain_max<-max(all_data$BS_gain)
  gain_median<-median(all_data$BS_gain)
  gain_mean<-mean(all_data$BS_gain)

############################
# Load model
############################

  model1 <- readRDS(file = "./output/models/model1.rds")
  model2 <- readRDS(file = "./output/models/model2.rds")

  # Calculate repeatability
         post_sd <- as_draws_df(model1, variable = "^sd", regex = TRUE)
       post_sd_C <- post_sd[,grepl("C", colnames(post_sd))]
       post_sd_E <- post_sd[,grepl("E", colnames(post_sd))]
    post_sd_cage <- post_sd[,grepl("cage", colnames(post_sd))]
     post_sd_sig <- as_draws_df(model1, variable = "^sigma", regex = TRUE)
    
  # Repeatability for the traits across treatment
    #Boldness
       R_boldness <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logboldness")
      
       R_bold_mean <- mean(R_boldness[,1])
        R_Blb_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[1], 2)
        R_Bub_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[2], 2)
      
      hist(R_boldness[,1])
      
    #Exploration
       R_explore <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "exploration")
      
       R_exp_mean<-mean(R_explore[,1])
       R_Blb_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[1], 2)
       R_Bub_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[2], 2)
       
       hist(R_explore[,1])
           
    #Activity
       R_activity <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logactivity")
      
       R_act_mean<-mean(R_activity[,1])
       R_Blb_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[1], 2)
       R_Bub_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[2], 2)
       
       hist(R_activity[,1])
      
  # Compare whether repeatability is different between exploratory and boldness
      R_contrast <- R_explore - R_boldness
        
# Repeatability for the traits between treatment

         post_sd <- as_draws_df(model2, variable = "^sd", regex = TRUE)
       post_sd_C <- post_sd[,grepl("C", colnames(post_sd))] #ID control
       post_sd_E <- post_sd[,grepl("E", colnames(post_sd))] #ID experimental
    post_sd_cage <- post_sd[,grepl("cage", colnames(post_sd))]
     post_sd_sig <- exp(as_draws_df(model2, variable = "^b_sigma", regex = TRUE))

    #my function doesn't work
R_C_bolness<- rep_each(post_sd_C_B, post_sd_cage, post_sig_B, trait = "logboldness")
R_C_boldness

############################
##     CONTROL GROUP
############################

#Boldness for control group
  R_C_boldness <-  post_sd_C[,grep("logboldness", colnames(post_sd_C))]^2  / (post_sd_sig[,grep("b_sigma_logboldness_treatmentC", colnames(post_sd_sig))]^2 +
                      post_sd_C[,grep("logboldness", colnames(post_sd_C))]^2 + 
                      post_sd_cage[ ,grep("logboldness", colnames(post_sd_cage))]^2)
#verification
  0.38^2 / (exp(-0.19)^2 + 0.38^2 + 0.19^2)

  hist(R_C_boldness[,1])
  
      R_C_bold <- mean(R_C_boldness[,1], 3)
  R_Blb_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for control group
  R_C_exploration <-  post_sd_C[,grep("exploration", colnames(post_sd_C))]^2  / (post_sd_sig[,grep("b_sigma_exploration_treatmentC", colnames(post_sd_sig))]^2 +
                      post_sd_C[,grep("exploration", colnames(post_sd_C))]^2 + 
                      post_sd_cage[ ,grep("exploration", colnames(post_sd_cage))]^2)
#verification
  0.58^2 / (exp(-0.12)^2 + 0.58^2 + 0.15^2) #same number

  hist(R_C_exploration[,1])
  mean(R_C_exploration[,1])
  R_Blb_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[2], 3)


#activity for control group
  R_C_activity <-  post_sd_C[,grep("logactivity", colnames(post_sd_C))]^2  / (post_sd_sig[,grep("b_sigma_logactivity_treatmentC", colnames(post_sd_sig))]^2 +
                      post_sd_C[,grep("logactivity", colnames(post_sd_C))]^2 + 
                      post_sd_cage[ ,grep("logactivity", colnames(post_sd_cage))]^2)
#verification
  0.65^2 / (exp(-0.13)^2 + 0.65^2 + 0.10^2) 

  hist(R_C_activity[,1])
  mean(R_C_activity[,1])
  R_Blb_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[2], 3)

############################
# EXPERIMENTAL GROUP
############################

#Boldness for experimental group
  R_E_boldness <-  post_sd_E[,grep("logboldness", colnames(post_sd_E))]^2  / (post_sd_sig[,grep("b_sigma_logboldness_treatmentE", colnames(post_sd_sig))]^2 +
                      post_sd_E[,grep("logboldness", colnames(post_sd_E))]^2 + 
                      post_sd_cage[ ,grep("logboldness", colnames(post_sd_cage))]^2)
#verification
  0.40^2 / (exp(-0.11)^2 + 0.40^2 + 0.19^2)

  hist(R_E_boldness[,1])
  mean(R_E_boldness[,1])
  R_Blb_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for experimental group
  R_E_exploration <-  post_sd_E[,grep("exploration", colnames(post_sd_E))]^2  / (post_sd_sig[,grep("b_sigma_exploration_treatmentE", colnames(post_sd_sig))]^2 +
                      post_sd_E[,grep("exploration", colnames(post_sd_E))]^2 + 
                      post_sd_cage[ ,grep("exploration", colnames(post_sd_cage))]^2)
#verification
  0.36^2 / (exp(-0.26)^2 + 0.36^2 + 0.15^2) 

  hist(R_E_exploration[,1])
  mean(R_E_exploration[,1])
  R_Blb_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[2], 3)

#activity for experimental group
R_E_activity <-  post_sd_E[,grep("logactivity", colnames(post_sd_E))]^2  / (post_sd_sig[,grep("b_sigma_logactivity_treatmentE", colnames(post_sd_sig))]^2 +
                     post_sd_E[,grep("logactivity", colnames(post_sd_E))]^2 + 
                     post_sd_cage[ ,grep("logactivity", colnames(post_sd_cage))]^2)

#verification
  0.49^2 / (exp(-0.26)^2 + 0.49^2 + 0.10^2) 

  hist(R_E_activity[,1])
  mean(R_E_activity[,1])
  R_Blb_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[2], 3)

#################################
# Compare R in E and C treatments
#################################

#Is repeatability different before and after treatment ? 
  p_value_bold<-pmcmc((R_C_boldness[,1]) - (R_E_boldness[,1])) # 0.95, meaning it's not different? Yes, not different

  # That makes sense given:
  par(mfrow = c(1,2))
  hist(R_E_boldness[,1])
  hist(R_C_boldness[,1])

  p_value_exp<-pmcmc((R_C_exploration[,1]) - (R_E_exploration[,1])) #not different
  p_value_act<-pmcmc((R_C_activity[,1]) - (R_E_activity[,1])) #not different

#Is the repeatability different from 0?

#Boldness control. No, NULL cannot be 5 because your vector is a proportion, so you're comparing diffient scales / units. R_C_bolness is a proportion and your null is set to be 5% which is on the percentage scale. Change as follows.
  p_value_bold_C<-pmcmc(R_C_boldness[,1]*100, null = 5)
#Boldness experimental
  p_value_bold_E<-pmcmc(R_E_boldness[,1]*100, null = 5)
#Exploration control
  p_value_exp_C<-pmcmc(R_C_exploration[,1]*100, null = 5)
#Exploration experimental
  p_value_exp_E<-pmcmc(R_E_exploration[,1]*100, null = 5)

#Activity control
  p_value_act_C<-pmcmc(R_C_activity[,1]*100, null = 5)
#Activity experimental
  p_value_act_E<-pmcmc(R_E_activity[,1]*100, null = 5)

```

The caging experiment successfully infected our treatment fish. Control fish that stayed in the laboratory had no alive parasite, which indicate that the praziquantel treatment was effective. The two most abundant species found in the experimentally infected fish were trematodes causing the blackspot disease (Trematoda: *Apophallus sp.* and *Uvulifer sp.*; min-max: `r BS_min`- `r BS_max`; median: `r BS_median`) and the bass tapeworm (Cestoda: *Proteocephalus ambloplites*; min-max: `r cestode_min` - `r cestode_max` ; median: `r cestode_median`). The most abundant species of trematode causing blackspots was *Apophallus sp*. (Binning, Lanthier, unpublished data), but *Uvulifer sp.* was found more frequently inside the muscles (MG, personal observations).Experimentally fish gained in mean `r gain_mean` blackspots, and were found on the fines, body, gills and inside the muscles. Bass tapeworm were mostly found in the liver, stomach and digestive tract, occasionally around the spleen (parasite count: 9), and rarely on the gills (parasite count: 3) or the heart (parasite count: 2). Unknown nematode species were found rarely in the body cavity (alive parasite count: 4).

The average repeatbility of each traits across trial were `r round(R_exp_mean)` (95% CI: `r R_Blb_bold` to `r R_Bub_bold`) for boldness; `r round(R_exp_mean)`(95% CI: `r R_Blb_exp` to `r R_Bub_exp`) for exploration; and `r round(R_act_mean)`(95% CI: `r R_Blb_act` to `r R_Bub_act`) for activity (tab1).

#### *Boldness*

```{r}
#| label: fig-fig1
#| fig-cap: Repeatbility of behavioural traits
#| 
hist(R_boldness[,1])
```

```{r, tbl-tab1}
#| label: tbl-tab1
#| tbl-cap: Repeatbility estimates for traits
tab1 <- data.frame(Trait = c("log_Boldness", "Exploration","log_Activity"), 
"Group_C" = c(mean(R_C_bolness[,1]), mean(R_C_exploration[,1]), mean(R_C_activity[,1])), 
"0.025_(C)" = c((R_Blb_bold_C),(R_Blb_exp_C), (R_Blb_act_C)), "0.975_(C)" = c((R_Bub_bold_C), (R_Bub_exp_C),(R_Bub_act_C)),
"Group_E" =  c(mean(R_E_bolness[,1]), mean(R_E_exploration[,1]), mean(R_E_activity[,1])),
"0.025_(E)" = c((R_Blb_bold_E), (R_Blb_exp_E), (R_Blb_act_E)), "0.975_(E)" = c((R_Bub_bold_E), (R_Bub_exp_E), (R_Bub_act_E)), "p_value" = c((p_value_bold), (p_value_exp), (p_value_act)))



gt(tab1) %>% cols_align(align="center")
gt(tab1) %>% tab_header(
    title = "Repeatability for each personality trait")
gt(tab1) %>% tab_spanner(
    label = "Treatment",
    columns = c("Group_C","X0.025_.C.","X0.975_.C.","Group_E","X0.025_.E.","X0.975_.E.")
  )
```
