---
format:
  docx: 
    reference-doc: "./bib/template.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
crossref:  
  fig-title: Figure    # (default is "Figure")
  tbl-title: Table   # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.   # (default is "Table")
editor_options: 
  chunk_output_type: console
---

# Results

```{r}
#| label: load_packages
#| output: false
#| warning: false

    source("./R/func.R")
    pacman::p_load(tidyverse, brms, glmmTMB, gt, posterior, gt, glue, dplyr,magrittr)
    options(digits = 3, scipen = 2)
```

```{r}
#| label: load_data
#| output: false
#| warning: false

############################
# Import processed data
#############################
  all_data <- read.table("./output/all_data_p.csv",header=T, sep=",")
  all_data
############################
# Parasite count
#############################
### Blackspots distribution
  hist(all_data$BS_post_tot)

# Blackspots info
  BS_min<-min(all_data$BS_post_tot)
  BS_max<-max(all_data$BS_post_tot)
  BS_median<-median(all_data$BS_post_tot)

### Cestodes distribution
  hist(all_data$P04_alive)

# Cestodes info
  cestode_min<-min(all_data$P04_alive)
  cestode_max<-max(all_data$P04_alive)
  cestode_median<-median(all_data$P04_alive)
  mean(all_data$P04_alive)

### Nematodes distribution
  hist(all_data$P013_alive)

# Nematodes info
  nematode_min<-min(all_data$P013_alive)
  nematode_max<-max(all_data$P013_alive)

### Looking at BS gained after infection
# Create new columns in the dataset
  all_data$BS_gain<- all_data$BS_post_tot - all_data$BS_pre

# BS gain distribution
  hist(all_data$BS_gain)

# BS gain info
  gain_min<-min(all_data$BS_gain) ### miscount, some fish have less BS after infection
  gain_max<-max(all_data$BS_gain)
  gain_median<-median(all_data$BS_gain)
  gain_mean<-mean(all_data$BS_gain)

############################
# Load model
############################

  model1 <- readRDS(file = "./output/models/model1.rds")
  model1.2 <- readRDS(file = "./output/models/model1.2.rds")
  model2 <- readRDS(file = "./output/models/model2.rds")
  
############################
# Average repeatability across trials
############################
post_sd <- as_draws_df(model1, variable = "^sd", regex = TRUE)
post_sd_C <- post_sd[,grepl("C", colnames(post_sd))]
post_sd_E <- post_sd[,grepl("E", colnames(post_sd))]
post_sd_cage <- post_sd[,grepl("cage", colnames(post_sd))]
post_sd_sig <- as_draws_df(model1, variable = "^sigma", regex = TRUE)
    
    #Boldness
       R_boldness <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logboldness")
      
       R_bold_mean <- mean(R_boldness[,1])
        R_Blb_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[1], 2)
        R_Bub_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[2], 2)
      
      hist(R_boldness[,1])
      
    #Exploration
       R_explore <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "exploration")
      
       R_exp_mean<-mean(R_explore[,1])
       R_Blb_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[1], 2)
       R_Bub_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[2], 2)
       
       hist(R_explore[,1])
           
    #Activity
       R_activity <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logactivity")
      
       R_act_mean<-mean(R_activity[,1])
       R_Blb_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[1], 2)
       R_Bub_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[2], 2)
       
       hist(R_activity[,1])
      
  # Compare whether repeatability is different between exploratory and boldness
      R_contrast <- R_explore - R_boldness
      hist(R_contrast[,1])
      
############################
# Repeatability C vs E
############################

         post_sd_2 <- as_draws_df(model2, variable = "^sd", regex = TRUE)
       post_sd_C_2 <- post_sd_2[,grepl("C", colnames(post_sd_2))] #ID control
       post_sd_E_2 <- post_sd_2[,grepl("E", colnames(post_sd_2))] #ID experimental
    post_sd_cage_2 <- post_sd_2[,grepl("cage", colnames(post_sd_2))]
     post_sd_sig_2 <- exp(as_draws_df(model2, variable = "^b_sigma", regex = TRUE))

############################
##     CONTROL GROUP
############################

#Boldness for control group
  R_C_boldness <-  post_sd_C_2[,grep("logboldness", colnames(post_sd_C_2))]^2  / (post_sd_sig_2[,grep("b_sigma_logboldness_treatmentC", colnames(post_sd_sig_2))]^2 +
                      post_sd_C_2[,grep("logboldness", colnames(post_sd_C_2))]^2 + 
                      post_sd_cage_2[ ,grep("logboldness", colnames(post_sd_cage_2))]^2)
#verification
  0.38^2 / (exp(-0.19)^2 + 0.38^2 + 0.19^2)

  hist(R_C_boldness[,1])
  
  R_C_bold <- mean(R_C_boldness[,1])
  R_Blb_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for control group
  R_C_exploration <-  post_sd_C_2[,grep("exploration", colnames(post_sd_C_2))]^2  / (post_sd_sig_2[,grep("b_sigma_exploration_treatmentC", colnames(post_sd_sig_2))]^2 +
                      post_sd_C_2[,grep("exploration", colnames(post_sd_C_2))]^2 + 
                      post_sd_cage_2[ ,grep("exploration", colnames(post_sd_cage_2))]^2)
#verification
  0.58^2 / (exp(-0.12)^2 + 0.58^2 + 0.15^2) #same number

  hist(R_C_exploration[,1])
  mean(R_C_exploration[,1])
  R_Blb_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[2], 3)


#activity for control group
  R_C_activity <-  post_sd_C_2[,grep("logactivity", colnames(post_sd_C_2))]^2  / (post_sd_sig_2[,grep("b_sigma_logactivity_treatmentC", colnames(post_sd_sig_2))]^2 +
                      post_sd_C_2[,grep("logactivity", colnames(post_sd_C_2))]^2 + 
                      post_sd_cage_2[ ,grep("logactivity", colnames(post_sd_cage_2))]^2)
#verification
  0.65^2 / (exp(-0.13)^2 + 0.65^2 + 0.10^2) 

  hist(R_C_activity[,1])
  mean(R_C_activity[,1])
  R_Blb_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[2], 3)

############################
# EXPERIMENTAL GROUP
############################

#Boldness for experimental group
  R_E_boldness <-  post_sd_E_2[,grep("logboldness", colnames(post_sd_E_2))]^2  / (post_sd_sig_2[,grep("b_sigma_logboldness_treatmentE", colnames(post_sd_sig_2))]^2 +
                      post_sd_E_2[,grep("logboldness", colnames(post_sd_E_2))]^2 + 
                      post_sd_cage_2[ ,grep("logboldness", colnames(post_sd_cage_2))]^2)
#verification
  0.40^2 / (exp(-0.11)^2 + 0.40^2 + 0.19^2)

  hist(R_E_boldness[,1])
  mean(R_E_boldness[,1])
  R_Blb_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for experimental group
  R_E_exploration <-  post_sd_E_2[,grep("exploration", colnames(post_sd_E_2))]^2  / (post_sd_sig_2[,grep("b_sigma_exploration_treatmentE", colnames(post_sd_sig_2))]^2 +
                      post_sd_E_2[,grep("exploration", colnames(post_sd_E_2))]^2 + 
                      post_sd_cage_2[ ,grep("exploration", colnames(post_sd_cage_2))]^2)
#verification
  0.36^2 / (exp(-0.26)^2 + 0.36^2 + 0.15^2) 
  summary(model2)

  hist(R_E_exploration[,1])
  mean(R_E_exploration[,1])
  R_Blb_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[2], 3)

#activity for experimental group
R_E_activity <-  post_sd_E_2[,grep("logactivity", colnames(post_sd_E_2))]^2  / (post_sd_sig_2[,grep("b_sigma_logactivity_treatmentE", colnames(post_sd_sig_2))]^2 +
                     post_sd_E_2[,grep("logactivity", colnames(post_sd_E_2))]^2 + 
                     post_sd_cage_2[ ,grep("logactivity", colnames(post_sd_cage_2))]^2)

#verification
  0.49^2 / (exp(-0.26)^2 + 0.49^2 + 0.10^2) 
summary(model2)
  
  hist(R_E_activity[,1])
  mean(R_E_activity[,1])
  R_Blb_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[2], 3)

#################################
# Compare R in E and C treatments
#################################

#Is the repeatability different before and after treatment ? 
  
  #Boldness
  p_value_bold<-pmcmc((R_C_boldness[,1]) - (R_E_boldness[,1])) # Not different
  # That makes sense given:
  par(mfrow = c(1,2))
  hist(R_E_boldness[,1])
  hist(R_C_boldness[,1])
  
  #Exploration
  p_value_exp<-pmcmc((R_C_exploration[,1]) - (R_E_exploration[,1])) #not different
  
  # Histograms
  hist(R_E_exploration[,1])
  hist(R_C_exploration[,1])
  
  #Activity
  p_value_act<-pmcmc((R_C_activity[,1]) - (R_E_activity[,1])) #not different
  
   # Histograms
  hist(R_E_activity[,1])
  hist(R_C_activity[,1])
  
  
#Is the repeatability different from 5?

#Boldness control
  p_value_bold_C<-pmcmc(R_C_boldness[,1]*100, null = 5, twotail = FALSE)#different from 5
#Boldness experimental
  p_value_bold_E<-pmcmc(R_E_boldness[,1]*100, null = 5, twotail = FALSE)#different from 5
#Average boldness
  p_value_bold_a<-pmcmc(R_boldness[,1]*100, null = 5, twotail = FALSE)#not different from 5
  
#Exploration control
  p_value_exp_C<-pmcmc(R_C_exploration[,1]*100, null = 5, twotail = FALSE)#not different
  
  hist(R_C_exploration[,1])
  hist(R_E_exploration[,1])
#Exploration experimental
  p_value_exp_E<-pmcmc(R_E_exploration[,1]*100, null = 5, twotail = FALSE)#different
#Average exploration
  p_value_exp_a<-pmcmc(R_explore[,1]*100, null = 5, twotail = FALSE)#not different

#Activity control
  p_value_act_C<-pmcmc(R_C_activity[,1]*100, null = 5, twotail = FALSE)#not different
  hist(R_C_activity[,1])
#Activity experimental
  p_value_act_E<-pmcmc(R_E_activity[,1]*100, null = 5, twotail = FALSE)#not different
#Activity average
  p_value_act_a<-pmcmc(R_activity[,1]*100, null = 5,twotail = FALSE) #still get 0 for this one
  
  
#################################
# Behavioural Syndromes
#################################
  
# Extract correlations from model
  post_cor  <- as_draws_df(model2, variable = "^cor", regex= TRUE)
  head(post_cor)

  
# Extract the C and E groups separately
  cor_bold_treatC <-   post_cor[,grep("treatmentC__[a-z]*_treatmentC", colnames(post_cor))]
  cor_bold_treatE <-   post_cor[,grep("treatmentE__[a-z]*_treatmentE", colnames(post_cor))]

# See if syndromes differ in C and E
  #how to you know if they are different? CI overlap?
  
  #Boldness and activity
  bsyn_b_act_C <- data.frame(cor_bold_treatC[,1]); mean(bsyn_b_act_C[,1]); quantile(bsyn_b_act_C[,1], c(0.025, 0.975))
  
  bsyn_b_act_E <- data.frame(cor_bold_treatE[,1]); mean(bsyn_b_act_E[,1]); quantile(bsyn_b_act_E[,1], c(0.025, 0.975))
  
  #Boldness and exploration
  bsyn_b_exp_C <- data.frame(cor_bold_treatC[,2]); mean(bsyn_b_exp_C[,1]); quantile(bsyn_b_exp_C[,1], c(0.025, 0.975))
  
  bsyn_b_exp_E <- data.frame(cor_bold_treatE[,2]); mean(bsyn_b_exp_E[,1]); quantile(bsyn_b_exp_E[,1], c(0.025, 0.975))
  
  #Activity and exploration
  bsyn_act_exp_C <- data.frame(cor_bold_treatC[,3]); mean(bsyn_act_exp_C[,1]); quantile(bsyn_act_exp_C[,1], c(0.025, 0.975))
  
  bsyn_act_exp_E <- data.frame(cor_bold_treatE[,3]); mean(bsyn_act_exp_E[,1]); quantile(bsyn_act_exp_E[,1], c(0.025, 0.975)) ####This one is weird!!

# Overall syndrome
  # Take average of the two treatments
    bsyn_b_act   <- cbind(bsyn_b_act_C[,1], bsyn_b_act_E[,1]); mean(rowMeans(bsyn_b_act)); quantile(rowMeans(bsyn_b_act), c(0.025, 0.975))

  # Pool the two MCMC chains from the treatments into a giant vector 32,000 rows (2*16,000)
    #Boldness and activity
    bsyn_b_act2  <- rbind(c(bsyn_b_act_C[,1], bsyn_b_act_E[,1])); mean(bsyn_b_act2); quantile(bsyn_b_act2, c(0.025, 0.975))
    
    #Boldness and exploration
    bsyn_b_exp  <- rbind(c(bsyn_b_exp_C[,1], bsyn_b_exp_E[,1])); mean(bsyn_b_exp); quantile(bsyn_b_exp, c(0.025, 0.975))
    
    #Activity and exploration
    bsyn_act_exp  <- rbind(c(bsyn_act_exp_C[,1], bsyn_act_exp_E[,1])); mean(bsyn_act_exp); quantile(bsyn_act_exp, c(0.025, 0.975))
    
#Values in model 1.2 for logactivity-boldness
    #estimate = -0.48
    #CI = -0.93, 0.18 ##pool is closest to model 1.2

```
## Methods
## *Statistical anylysis*

All statistical analyses were performed with the software R (version 4.2.2). Adjusted fish mass was calculated as the fish mass minus parasite mass (Lagrue and Poulin, 2015). Parasite mass was estimated with the mean mass of 20 parasites (Vic, in prep). For bass tapeworm, adult average was 0.003g and larval form was 0.0008g. We decided to exclude nematodes since the mass varies grandly between individuals and is found rarely in our fish. Blackspots mass was considered too small to be subtracted from total mass (10^-7g). Body condition was calculated with the Fulton index (mass/standard length3 in cm) (Jakob, 1996) using the adjusted fish mass for the 2 measures of body condition after the experimental infection (we assume there is no parasite before the experimental infection). 

Exploration was distributed normally. Activity and boldness were log-transformed to impose normality. All variable were z-scaled. We fitted our models with a Bayesian statistical inference using 4 chains with an iteration of 6000 and a warm up of 2000. We visually inspected the MCMC sampling to see if the sampling ...(?) 

To test if we find evidence of personality and behavioural syndromes between traits, we built a model with the personality traits as response variables, treatment as a fixed effect, and fish ID and cage number as random effects. Model 1 had tank effect as a fixed factor compared to Model 2. We compared the models using the loo package. Model 2 was better fitted and we decided not to include tank effect in our models. 

To test if the experimental infection had an effect on personality, we sublet the dataset according to treatment. We used our dataset for the experimental group in model 3 and 4 to see if parasite load had a significative effect on the traits responses. Parasite load was included as a fixed factor; fish ID and cage were random factors. Model 3 assume than parasite load effect is linear, so we included parasite load^2 as a fixed factor in model 4. We compared model 3 and 4 using the loo method (should we do that?). We fitted model 5 with ID and cage as random effects for our control group. Finally, Model 6 used body condition as the response variable … 

#this could go with the paragraph about model 1? 
Repeatability (R) was calculated using the squared standard deviation for fish ID divided by the squared standard deviation for fish ID, cage and sigma from model 2 for each treatment group and for the average across groups. 
To estimate if repeatability was different from 0, we choose 0.05 as a threshold since the values can't be 0 in the distribution. Correlation between traits were extracted from model 2 to determine if there was a behavioural syndrome between traits. To measure the average correlation for each group, we pooled the two MCMC chains from the treatments into a giant vector 32,000 rows. 

### Results
#### *Experimental infection*

The caging experiment successfully infected our treatment fish. Control fish that stayed in the laboratory had no alive parasite, which indicate that the praziquantel treatment was effective. The two most abundant species found in the experimentally infected fish were trematodes causing the blackspot disease (Trematoda: *Apophallus sp.* and *Uvulifer sp.*; min-max: `r BS_min`- `r BS_max`; median: `r BS_median`) and the bass tapeworm (Cestoda: *Proteocephalus ambloplites*; min-max: `r cestode_min` - `r cestode_max` ; median: `r cestode_median`). The most abundant species of trematode causing blackspots was *Apophallus sp*. (Binning, Lanthier, unpublished data), but *Uvulifer sp.* was found more frequently inside the muscles (MG, personal observations).Experimentally fish gained in mean `r gain_mean` blackspots, and were found on the fines, body, gills and inside the muscles. Bass tapeworm were mostly found in the liver, stomach and digestive tract, occasionally around the spleen (parasite count: 9), and rarely on the gills (parasite count: 3) or the heart (parasite count: 2). Unknown nematode species were found rarely in the body cavity (alive parasite count: 4).

#### *Evidence of personality and behavioural syndrome*

Boldness, exploration and activity were all repeatable accross trials (Boldness: `r mean(R_boldness[,1])`, 95% CI: `r R_Blb_bold` to `r R_Bub_bold`, $pMCMC_{\alpha = 0.05}$ = `r p_value_bold_a`; Exploration: `r mean(R_explore[,1])`, 95% CI: `r R_Blb_exp` to `r R_Bub_exp`, $pMCMC_{\alpha = 0.05}$ = `r p_value_exp_a`; Activity: `r mean(R_activity[,1])`, 95% CI: `r R_Blb_act` to `r R_Bub_act`, $pMCMC_{\alpha = 0.05}$ = `r p_value_act_a`). 
We did not observe among-individual variation to be higher in the control vs experimentally infected groups (@tbl-tab1). Repeatability did not differ between treatment for boldness (p-value = `r p_value_bold`), exploration (p-value: `r p_value_exp`) and activity (p-value:`r p_value_act`). 

#### *Behavioural syndrome*

summary(model1.2)


```{r}
#| echo: false
#| include: false
summary(model2)
summary(model1)
```

#### *Effect of parasite*

#### *Boldness*

```{r}
#| label: fig-fig1
#| fig-cap: Repeatbility of behavioural traits
#| 
hist(R_boldness[,1])
```



```{r}
#| label: tbl-tab1
#| tbl-cap: Repeatbility estimates for traits
#| 
tab1 <- data.frame(Trait = c("Boldness (log)", "Exploration","Activity (log)"), 
                "Group C" = c(mean(R_C_boldness[,1]), mean(R_C_exploration[,1]), mean(R_C_activity[,1])), 
                  "2.5% CI (C)" = c((R_Blb_bold_C),(R_Blb_exp_C), (R_Blb_act_C)),
              "9.75% CI (C)" = c((R_Bub_bold_C), (R_Bub_exp_C),(R_Bub_act_C)),
                "Group E" = c(mean(R_E_boldness[,1]), mean(R_E_exploration[,1]), mean(R_E_activity[,1])),
              "2.5% CI (E)" = c((R_Blb_bold_E), (R_Blb_exp_E), (R_Blb_act_E)), "9.75% CI (E)" = c((R_Bub_bold_E), (R_Bub_exp_E), (R_Bub_act_E)),           
                "p_value" = c((p_value_bold), (p_value_exp), (p_value_act)), check.names = FALSE)

gt(tab1) 

```
