---
format:
  docx: 
    reference-doc: "./bib/template.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
crossref:  
  fig-title: Figure    # (default is "Figure")
  tbl-title: Table   # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.   # (default is "Table")
editor_options: 
  chunk_output_type: console
---

# Results

```{r}
#| label: load_packages
#| output: false
#| warning: false

    source("./R/func.R")
    pacman::p_load(tidyverse, brms, glmmTMB, gt, latex2exp, posterior, gt, glue, dplyr,magrittr, ggplot2, cowplot)
    options(digits = 3, scipen = 2)
    
```

```{r}
#| label: load_data and models
#| output: false
#| warning: false

############################
# Import processed data
#############################
  all_data <- read.table("./output/all_data_p.csv",header=T, sep=",")

############################
# Load model
############################

  model1 <- readRDS(file = "./output/models/model1.rds")
  model1.2 <- readRDS(file = "./output/models/model1.2.rds")
  model2 <- readRDS(file = "./output/models/model2.rds")
  model2.2 <- readRDS(file = "./output/models/model2.2.rds")
  model3 <- readRDS(file = "./output/models/model_3.rds")
 
  R2_m_3 <- bayes_R2(model3, re.form = NA) #marginal
  R2_c_3 <- bayes_R2(model3) #conditional
  
  model4 <- readRDS(file = "./output/models/model_4.rds")
  model5 <- readRDS(file = "./output/models/model_5.rds")
  
  R2_m_5 <- bayes_R2(model5, re.form = NA) #marginal
  R2_c_5 <- bayes_R2(model5) #conditional
  
  model6 <- readRDS(file = "./output/models/model_6.rds")
  
  R2_m_6 <- bayes_R2(model6, re.form = NA) #marginal
  R2_c_6 <- bayes_R2(model6) #conditional
  
  model7 <- readRDS(file = "./output/models/model_7.rds")
  R2_m_7 <- bayes_R2(model7, re.form = NA) #marginal
  R2_c_7 <- bayes_R2(model7) #conditional
  
  #Compare model 3 and 6 (only thing that changed was body condition)
  loo(model3,model6) #model 6 better but they are really close
  
  model8<-readRDS(file = "./output/models/model_8.rds")
  model9<-readRDS(file = "./output/models/model_9.rds")

```

```{r}
#| label: Repeatability and behavioral syndromes
#| output: false
#| warning: false

############################
# Parasite count
#############################
### Blackspots distribution
  hist(all_data$BS_post_tot)

# Blackspots info
  BS_min<-min(all_data$BS_post_tot)
  BS_max<-max(all_data$BS_post_tot)
  BS_median<-median(all_data$BS_post_tot)

### Cestodes distribution
  hist(all_data$P04_alive)

# Cestodes info
  cestode_min<-min(all_data$P04_alive)
  cestode_max<-max(all_data$P04_alive)
  cestode_median<-median(all_data$P04_alive)
  mean(all_data$P04_alive)

### Nematodes distribution
  hist(all_data$P013_alive)

# Nematodes info
  nematode_min<-min(all_data$P013_alive)
  nematode_max<-max(all_data$P013_alive)

### Looking at BS gained after infection
# Create new columns in the dataset
  all_data$BS_gain<- all_data$BS_post_tot - all_data$BS_pre

# BS gain distribution
  hist(all_data$BS_gain)

# BS gain info
  gain_min<-min(all_data$BS_gain) ### miscount, some fish have less BS after infection
  gain_max<-max(all_data$BS_gain)
  gain_median<-median(all_data$BS_gain)
  gain_mean<-mean(all_data$BS_gain)


############################
# Repeatability C vs E
############################

         post_sd_2 <- as_draws_df(model2, variable = "^sd", regex = TRUE)
       post_sd_C_2 <- post_sd_2[,grepl("C", colnames(post_sd_2))] #ID control
       post_sd_E_2 <- post_sd_2[,grepl("E", colnames(post_sd_2))] #ID experimental
    post_sd_cage_2 <- post_sd_2[,grepl("cage", colnames(post_sd_2))]
     post_sd_sig_2 <- as_draws_df(model2, variable = "^b_sigma", regex = TRUE)
     post_sd_sig_C_2 <- exp(post_sd_sig_2[,grepl("C", colnames(post_sd_sig_2))]) #ID control
       post_sd_sig_E_2 <- exp(post_sd_sig_2[,grepl("E", colnames(post_sd_sig_2))]) #ID experimental

############################
##     CONTROL GROUP
############################

#Boldness for control group
  fish_c_b <- post_sd_C_2[,grep("logboldness", colnames(post_sd_C_2))]^2
  cage_c_b <- post_sd_cage_2[ ,grep("logboldness", colnames(post_sd_cage_2))]^2
   res_c_b <- post_sd_sig_C_2[,grep("b_sigma_logboldness_treatmentC", colnames(post_sd_sig_C_2))]^2

  R_C_boldness <-   fish_c_b / (fish_c_b + cage_c_b + res_c_b)

#verification
 0.40^2 / (0.15^2 + 0.40^2 + exp(-0.14)^2)
 
  hist(R_C_boldness[,1])
  R_C_bold <- mean(R_C_boldness[,1])
  R_Blb_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for control group
  fish_c_ex <- post_sd_C_2[,grep("exploration", colnames(post_sd_C_2))]^2
  cage_c_ex <- post_sd_cage_2[ ,grep("exploration", colnames(post_sd_cage_2))]^2
   res_c_ex <- post_sd_sig_C_2[,grep("b_sigma_exploration_treatmentC", colnames(post_sd_sig_C_2))]^2

  R_C_exploration <-   fish_c_ex / (fish_c_ex + cage_c_ex + res_c_ex)
  
#verification
  0.57^2 / (exp(-0.11)^2 + 0.57^2 + 0.16^2) #same number

  hist(R_C_exploration[,1])
  mean(R_C_exploration[,1])
  R_Blb_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[2], 3)

#activity for control group
  fish_c_ac <- post_sd_C_2[,grep("logactivity", colnames(post_sd_C_2))]^2
  cage_c_ac <- post_sd_cage_2[ ,grep("logactivity", colnames(post_sd_cage_2))]^2
  res_c_ac <- post_sd_sig_C_2[,grep("b_sigma_logactivity_treatmentC", colnames(post_sd_sig_C_2))]^2

  R_C_activity <-   fish_c_ac / (fish_c_ac + cage_c_ac + res_c_ac)
  
#verification
  0.64^2 / (exp(-0.15)^2 + 0.64^2 + 0.11^2) 

  hist(R_C_activity[,1])
  mean(R_C_activity[,1])
  R_Blb_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[2], 3)

############################
# EXPERIMENTAL GROUP
############################

#Boldness for experimental group
  fish_e_b <- post_sd_E_2[,grep("logboldness", colnames(post_sd_E_2))]^2
  cage_e_b <- post_sd_cage_2[ ,grep("logboldness", colnames(post_sd_cage_2))]^2
  res_e_b <- post_sd_sig_E_2[,grep("b_sigma_logboldness_treatmentE", colnames(post_sd_sig_E_2))]^2

  R_E_boldness <-   fish_e_b / (fish_e_b + cage_e_b + res_e_b)
  
#verification
  0.42^2 / (exp(-0.11)^2 + 0.42^2 + 0.15^2)

  hist(R_E_boldness[,1])
  mean(R_E_boldness[,1])
  R_Blb_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for experimental group
   fish_e_ex <- post_sd_E_2[,grep("exploration", colnames(post_sd_E_2))]^2
  cage_e_ex <- post_sd_cage_2[ ,grep("exploration", colnames(post_sd_cage_2))]^2
  res_e_ex <- post_sd_sig_E_2[,grep("b_sigma_exploration_treatmentE", colnames(post_sd_sig_E_2))]^2

  R_E_exploration <-   fish_e_ex / (fish_e_ex + cage_e_ex + res_e_ex)
  
#verification
  0.38^2 / (exp(-0.28)^2 + 0.38^2 + 0.16^2) 

  hist(R_E_exploration[,1])
  mean(R_E_exploration[,1])
  R_Blb_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[2], 3)

#activity for experimental group
  fish_e_ac <- post_sd_E_2[,grep("logactivity", colnames(post_sd_E_2))]^2
  cage_e_ac <- post_sd_cage_2[ ,grep("logactivity", colnames(post_sd_cage_2))]^2
  res_e_ac <- post_sd_sig_E_2[,grep("b_sigma_logactivity_treatmentE", colnames(post_sd_sig_E_2))]^2

  R_E_activity <-   fish_e_ac / (fish_e_ac + cage_e_ac + res_e_ac)

#verification
  0.51^2 / (exp(-0.26)^2 + 0.51^2 + 0.11^2) 
  
  hist(R_E_activity[,1])
  mean(R_E_activity[,1])
  R_Blb_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[2], 3)

#############################
# Overall Repeatability
#############################

  # Boldness
   R_bold  <-  overall_repeatability(post_sd_C_2, post_sd_E_2, post_sd_cage_2, post_sd_sig_C_2, post_sd_sig_E_2, trait = "logboldness")
  
        R_bold_mean <- mean(R_bold)
        R_Blb_bold <- round(quantile(R_bold, c(0.025, 0.975))[1], 2)
        R_Bub_bold <- round(quantile(R_bold, c(0.025, 0.975))[2], 2)
        
  #Exploration
  R_exp  <-  overall_repeatability(post_sd_C_2, post_sd_E_2, post_sd_cage_2, post_sd_sig_C_2, post_sd_sig_E_2, trait = "exploration")
  
      R_exp_mean<-mean(R_exp)
       R_Blb_exp <- round(quantile(R_exp, c(0.025, 0.975))[1], 2)
       R_Bub_exp <- round(quantile(R_exp, c(0.025, 0.975))[2], 2)
       
  #Activity
  R_act  <-  overall_repeatability(post_sd_C_2, post_sd_E_2, post_sd_cage_2, post_sd_sig_C_2, post_sd_sig_E_2, trait = "logactivity")
  
  R_act_mean<-mean(R_act)
       R_Blb_act <- round(quantile(R_act, c(0.025, 0.975))[1], 2)
       R_Bub_act <- round(quantile(R_act, c(0.025, 0.975))[2], 2)

#################################
# Compare R in E and C treatments
#################################

#Is the repeatability different before and after treatment ? 
  
  #Boldness
  p_value_bold<-pmcmc((R_C_boldness[,1]) - (R_E_boldness[,1])) # Not different
  # That makes sense given:
  par(mfrow = c(1,2))
  hist(R_E_boldness[,1])
  hist(R_C_boldness[,1])
  
  #Exploration
  p_value_exp<-pmcmc((R_C_exploration[,1]) - (R_E_exploration[,1])) #not different
  
  # Histograms
  hist(R_E_exploration[,1])
  hist(R_C_exploration[,1])
  
  #Activity
  p_value_act<-pmcmc((R_C_activity[,1]) - (R_E_activity[,1])) #not different
  
   # Histograms
  hist(R_E_activity[,1])
  hist(R_C_activity[,1])
  
  
#Is the repeatability different from 5?

#Boldness control
  p_value_bold_C<-pmcmc(R_C_boldness[,1]*100, null = 5, twotail = FALSE)#not significative
#Boldness experimental
  p_value_bold_E<-pmcmc(R_E_boldness[,1]*100, null = 5, twotail = FALSE)#not significative
#Average boldness
  p_value_bold_a<-pmcmc(R_bold*100, null = 5, twotail = FALSE)#not significative but really close
  
#Exploration control
  p_value_exp_C<-pmcmc(R_C_exploration[,1]*100, null = 5, twotail = FALSE)#significative
  
  hist(R_C_exploration[,1])
  hist(R_E_exploration[,1])
#Exploration experimental
  p_value_exp_E<-pmcmc(R_E_exploration[,1]*100, null = 5, twotail = FALSE)#not significative
#Average exploration
  p_value_exp_a<-pmcmc(R_exp*100, null = 5, twotail = FALSE)#significative

#Activity control
  p_value_act_C<-pmcmc(R_C_activity[,1]*100, null = 5, twotail = FALSE)##significative
  hist(R_C_activity[,1])
#Activity experimental
  p_value_act_E<-pmcmc(R_E_activity[,1]*100, null = 5, twotail = FALSE)#significative
#Activity average
  p_value_act_a<-pmcmc(R_act*100, null = 5,twotail = FALSE) #significative
  
  
#################################
# Behavioural Syndromes
#################################
  
# Extract correlations from model
  post_cor  <- as_draws_df(model2, variable = "^cor", regex= TRUE)
  head(post_cor)

# Extract the C and E groups separately
  cor_bold_treatC <-   post_cor[,grep("treatmentC__[a-z]*_treatmentC", colnames(post_cor))]
  cor_bold_treatE <-   post_cor[,grep("treatmentE__[a-z]*_treatmentE", colnames(post_cor))]

# See if syndromes differ in C and E
  #how to you know if they are different? CI overlap?
  
  #Boldness and activity
  bsyn_b_act_C <- data.frame(cor_bold_treatC[,1]); mean(bsyn_b_act_C[,1]); quantile(bsyn_b_act_C[,1], c(0.025, 0.975))
  
  bsyn_b_act_E <- data.frame(cor_bold_treatE[,1]); mean(bsyn_b_act_E[,1]); quantile(bsyn_b_act_E[,1], c(0.025, 0.975))
  
  pmcmc_b_act_E<-pmcmc(bsyn_b_act_E[,1], twotail = TRUE)
  pmcmc_b_act_C<-pmcmc(bsyn_b_act_C[,1], twotail = TRUE)
  
  #is the difference significant
   pmcmc_b_act<-pmcmc(bsyn_b_act_C[,1] - bsyn_b_act_E[,1], twotail = TRUE) #no
  
  #Boldness and exploration
  bsyn_b_exp_C <- data.frame(cor_bold_treatC[,2]); mean(bsyn_b_exp_C[,1]); quantile(bsyn_b_exp_C[,1], c(0.025, 0.975))
  
  bsyn_b_exp_E <- data.frame(cor_bold_treatE[,2]); mean(bsyn_b_exp_E[,1]); quantile(bsyn_b_exp_E[,1], c(0.025, 0.975))
  
  #is the difference significant
  pmcmc_b_exp<-pmcmc(bsyn_b_exp_C[,1] - bsyn_b_exp_E[,1], twotail = TRUE) #no
  
  #Activity and exploration
  bsyn_act_exp_C <- data.frame(cor_bold_treatC[,3]); mean(bsyn_act_exp_C[,1]); quantile(bsyn_act_exp_C[,1], c(0.025, 0.975))
  
  pmcmc_act_exp_C<- pmcmc(bsyn_act_exp_C[,1], twotail = TRUE) #significant
  
  bsyn_act_exp_E <- data.frame(cor_bold_treatE[,3]); mean(bsyn_act_exp_E[,1]); quantile(bsyn_act_exp_E[,1], c(0.025, 0.975))  
  
   pmcmc_act_exp_E<- pmcmc(bsyn_act_exp_E[,1], twotail = TRUE) #not significant

  #is the difference significant
 pmcmc_act_exp<- pmcmc(bsyn_act_exp_C[,1] - bsyn_act_exp_E[,1], twotail = TRUE) #no
  
# Overall syndrome
  # Take average of the two treatments
    bsyn_b_act   <- cbind(bsyn_b_act_C[,1], bsyn_b_act_E[,1]); mean(rowMeans(bsyn_b_act)); quantile(rowMeans(bsyn_b_act), c(0.025, 0.975))

  # Pool the two MCMC chains from the treatments into a giant vector 32,000 rows (2*16,000)
    #Boldness and activity
bsyn_b_act2  <- rbind(c(bsyn_b_act_C[,1], bsyn_b_act_E[,1]))
mean(bsyn_b_act2)
q_b_act<-quantile(bsyn_b_act2, c(0.025, 0.975))
    
    #Boldness and exploration
bsyn_b_exp  <- rbind(c(bsyn_b_exp_C[,1], bsyn_b_exp_E[,1]))
mean(bsyn_b_exp)
q_b_exp<-quantile(bsyn_b_exp, c(0.025, 0.975))
    
    #Activity and exploration
bsyn_act_exp  <- rbind(c(bsyn_act_exp_C[,1], bsyn_act_exp_E[,1]))
mean(bsyn_act_exp)
q_act_exp<-quantile(bsyn_act_exp, c(0.025, 0.975))
    
#Values in model 1.2 for logactivity-boldness
    #estimate = -0.48
    #CI = -0.93, 0.18 ##pool is closest to model 1.2

    
```

### Methods
#### *Statistical analysis*

All statistical analyses were performed with the software R (version 4.2.2). Adjusted fish mass was calculated as the fish mass minus parasite mass (Lagrue and Poulin, 2015). Parasite mass was estimated with the mean mass of 20 parasites (Vic, in prep). For bass tapeworm, adult average mass was 0.003g and larval form was 0.0008g. We decided to exclude nematodes since the mass varies grandly between individuals and is found rarely in our fish. Blackspots mass was considered too small to be subtracted from total mass ($10^{-7}g$). Body condition was calculated with the Fulton index ($mass/length^3$) (Jakob, 1996). We had 4 measures of body condition, one for each trial (measured closest to the trial). We used the adjusted fish mass for the 2 measures of body condition after the experimental infection (we assume there is no parasite before the experimental infection). We used standard length of the fish in centimeters. We calculated parasite load by adding the total number of blackspots post-infection with the total number of cestodes found alive (adult and larvae form). We could not determine if larvae form was alive or not visually, but we assumed it can have an effect if the larva is developping in the fish. 

Exploration was distributed normally visually. Activity and boldness were log-transformed to impose normality. All variable were z-scaled before fitting the models. We fitted our models with a Bayesian statistical inference using 4 chains with an iteration of 6000 and a warm up of 2000. We visually inspected the MCMC sampling to see if the sampling ...(?) 

To test if we find evidence of personality and behavioural syndromes between traits, we built a model (n = 264) with traits as response variables, treatment (uninfected vs infected) as a fixed effect, fish ID and cage number as random effects. Model 1 had tank effect as a fixed factor compared to Model 2. We compared the models using the loo package. Model 2 was better fitted than model 1 and we decided not to include tank effect in our models. Repeatability (R) was calculated using the squared standard deviation for fish ID divided by the squared standard deviation for fish ID, cage and sigma from the posterior distribution of model 2 for each treatment group and across groups. To estimate if repeatability was different from 0, we choose 0.05 as a threshold since the values can't be 0 in the distribution. Correlation between traits were extracted from the posterior distribution of model 2 to determine if there was a behavioural syndrome between traits. To measure the average correlation for each group, we pooled together the two MCMC chains for both group.

To test if the experimental infection had an effect on personality, we sublet the data set according to the treatment (uninfected/pre-infection: n = 144; infected/post-infection: n = 120). We built Model 3 to see if parasite load have an effect on the traits. Parasite load was included as a fixed factor, fish ID and cage number as random factors. Model 3 assume than parasite load effect is linear, so we included parasite $load^2$ as a fixed factor in model 4. Our sample was too small to estimate model 4. 

To test if body condition as an effect on traits, we fitted model 5 with body condition as a fixed factor, ID and cage number as random effects for our uninfected group. Model 6 was fitted with parasite load and body condition for our infected group. Finally, to see if the parasite species have different effects on the traits, we built model 7 with total of cestodes, total of blackspots and body condition as fixed factors; ID and cage number as random factors. 

### Results
#### *Experimental infection*

The caging experiment successfully infected our fish. Control fish that stayed in the laboratory had no alive parasite, which indicate that the praziquantel treatment was effective. The two most abundant species found in the experimentally infected fish were trematodes causing the blackspot disease (Trematoda: *Apophallus sp.* and *Uvulifer sp.*; min-max: `r BS_min`- `r BS_max`; median: `r BS_median`) and the bass tapeworm (Cestoda: *Proteocephalus ambloplites*; min-max: `r cestode_min` - `r cestode_max` ; median: `r cestode_median`). The most abundant species of trematode causing blackspots was *Apophallus sp*. (Binning, Lanthier, unpublished data), but *Uvulifer sp.* was found more frequently inside the muscles (MG, personal observations).Experimentally fish gained in mean `r gain_mean` blackspots, and were found on the fines, body, gills and inside the muscles. Bass tapeworm were mostly found in the liver, stomach and digestive tract, occasionally around the spleen (parasite count: 9), and rarely on the gills (parasite count: 3) or the heart (parasite count: 2). Unknown nematode species were found rarely in the body cavity (alive parasite count: 4).

#### *Evidence of personality and behavioural syndromes*

Exploration and activity were repeatable across trials (Exploration: R = `r R_exp_mean`, 95% CI = `r R_Blb_exp`, `r R_Bub_exp`, $pMCMC_{\alpha = 0.05}$ = `r p_value_exp_a`; Activity: R = `r R_act_mean`, 95% CI = `r R_Blb_act`, `r R_Bub_act`, $pMCMC_{\alpha = 0.05}$ = `r p_value_act_a`), but boldness was not significantly repeatable (Boldness: R = `r R_bold_mean`, 95% CI = `r R_Blb_bold`, `r R_Bub_bold`, $pMCMC_{\alpha = 0.05}$ = `r p_value_bold_a`). We did not observe among-individual variation to be higher in the uninfected vs experimentally infected group (@tbl-tab1). Repeatability did not differ between treatment for boldness ($pMCMC_{\alpha = 0.05}$ = `r p_value_bold`), exploration ($pMCMC_{\alpha = 0.05}$ = `r p_value_exp`) and activity ($pMCMC_{\alpha = 0.05}$ = `r p_value_act`).We found evidence of behavioural syndromes between boldness and activity (cor = `r mean(bsyn_b_act2)`, 95% CI = `r q_b_act`); boldness and exploration (cor = `r mean(bsyn_b_exp)`, 95% CI = `r q_b_exp`), and between activity and exploration (cor = `r mean(bsyn_act_exp)`, 95% CI = `r q_act_exp`)  The correlation did not differ between the uninfected and experimentally infected group for these syndromes (Boldness-Activity: $pMCMC_{\alpha = 0.05}$ =  `r pmcmc_b_act`; Boldness-Exploration: $pMCMC_{\alpha = 0.05}$ =  `r pmcmc_b_exp`; Activity-Exploration: $pMCMC_{\alpha = 0.05}$ =  `r pmcmc_act_exp`).


```{r}
#| label: parasite effects
#| output: false
#| warning: false

#################################
# MODEL 3: effect of parasite on experimental group
#################################
  
#Extract post sd from model 3
post_sd_pl <- as_draws_df(model3, variable = "^b", regex = TRUE)

#extrait effect of parasite load on each traits
bold_pl<-post_sd_pl[,grep("b_logboldness_z_pl", colnames(post_sd_pl))]
exp_pl<-post_sd_pl[,grep("b_exploration_z_pl", colnames(post_sd_pl))]
act_pl<-post_sd_pl[,grep("b_logactivity_z_pl", colnames(post_sd_pl))]

  #mean and quantile
  act_pl_num<- as.numeric(unlist(act_pl))
  act_pl_mean <- mean(act_pl_num)
  act_pl_Blb <- round(quantile(act_pl_num, c(0.025, 0.975))[1], 3)
  act_pl_Bub <- round(quantile(act_pl_num, c(0.025, 0.975))[2], 3)
  
  #pmcmc value
  p_act_pl<-pmcmc(act_pl_num, twotail = TRUE) #significant

  #R2
  R2_m_3 <- bayes_R2(model3, re.form = NA) #marginal
  R2_c_3 <- bayes_R2(model3) #conditional
  
  
#################################
# MODEL 5: body condition on control group
#################################
  
#Extract post sd from model 5
post_sd_bc <- as_draws_df(model5, variable = "^b", regex = TRUE)

#extrait effect of parasite load on each traits
bold_bc<-post_sd_bc[,grep("b_logboldness_z_bc", colnames(post_sd_bc))]
exp_bc<-post_sd_bc[,grep("b_exploration_z_bc", colnames(post_sd_bc))]
act_bc<-post_sd_bc[,grep("b_logactivity_z_bc", colnames(post_sd_bc))]

  #mean and quantile for activity 
  act_bc_num<- as.numeric(unlist(act_bc))
  act_bc_mean <- mean(act_bc_num)
  act_bc_Blb <- round(quantile(act_bc_num, c(0.025, 0.975))[1], 3)
  act_bc_Bub <- round(quantile(act_bc_num, c(0.025, 0.975))[2], 3)
  
  #pmcmc value for activity
  p_act_bc<-pmcmc(act_bc_num, twotail = TRUE) #significant

  #R2
  R2_m_5 <- bayes_R2(model5, re.form = NA) #marginal
  R2_c_5 <- bayes_R2(model5) #conditional
  
  #mean and quantile for exploration
  exp_bc_num<- as.numeric(unlist(exp_bc))
  exp_bc_mean <- mean(exp_bc_num)
  exp_bc_Blb <- round(quantile(exp_bc_num, c(0.025, 0.975))[1], 3)
  exp_bc_Bub <- round(quantile(exp_bc_num, c(0.025, 0.975))[2], 3)
  
  #pmcmc value for exploration
  p_exp_bc<-pmcmc(exp_bc_num, twotail = TRUE) 

  #mean and quantile for boldness
  bold_bc_num<- as.numeric(unlist(bold_bc))
  bold_bc_mean <- mean(bold_bc_num)
  bold_bc_Blb <- round(quantile(bold_bc_num, c(0.025, 0.975))[1], 3)
  bold_bc_Bub <- round(quantile(bold_bc_num, c(0.025, 0.975))[2], 3)
  
  #pmcmc value for activity
  p_bold_bc<-pmcmc(bold_bc_num, twotail = TRUE) 

  
  
#################################
# MODEL 6: body condition and parasite load on infected fish
#################################
#Extract post sd from model 6
post_sd_pl_bc<- as_draws_df(model6, variable = "^b", regex = TRUE)

#extrait effect of body condition and parasite load on each traits
bold_bc_6<-post_sd_pl_bc[,grep("b_logboldness_z_bc", colnames(post_sd_pl_bc))]
exp_bc_6<-post_sd_pl_bc[,grep("b_exploration_z_bc", colnames(post_sd_pl_bc))]
act_bc_6<-post_sd_pl_bc[,grep("b_logactivity_z_bc", colnames(post_sd_pl_bc))]

  #mean and quantile for activity 
  act_bc_num_6<- as.numeric(unlist(act_bc))
  act_bc_mean_6 <- mean(act_bc_num)
  act_bc_Blb_6 <- round(quantile(act_bc_num, c(0.025, 0.975))[1], 3)
  act_bc_Bub_6 <- round(quantile(act_bc_num, c(0.025, 0.975))[2], 3)
  
  #pmcmc value for activity
  p_act_bc_6<-pmcmc(act_bc_num, twotail = TRUE) #significant

  #R2
  R2_m_5 <- bayes_R2(model6, re.form = NA) #marginal
  R2_c_5 <- bayes_R2(model6) #conditional
  R2_c_5 1,1
  
#################################
# MODEL 7: looking at two species of parasites
#################################
  
#################################
# MODEL 8: interaction between body condition and parasite load
#################################
  
#################################
# MODEL 9: interaction between BS and cestodes
#################################
  
  
```

#### *Parasites effects  on personality traits*

Body condition had a positive effect on activity in both the uninfected and experimentally infected group (Uninfected: $\Beta$ = `r act_bc_mean`, 95% CI = `r act_bc_Blb`, `r act_bc_Bub`, $pMCMC_{\alpha = 0.05}$ = `r p_act_bc`, $R_{^2}$ = 0.046), Infected: $\Beta$ = `r act_bc_mean_6`, 95% CI = `r act_bc_Blb_6`, `r act_bc_Bub_6`, $pMCMC_{\alpha = 0.05}$ = `r p_act_bc_6`, $R_{^2}$ = 0.143)). Body condition did not have a significant effect on boldness or exploration in the uninfected group () and infected group ().


When looking at the experimentally infected fish, parasite load had a negative effect on activity ($\Beta$ = `r act_pl_mean`, 95% CI = `r act_pl_Blb`, `r act_pl_Bub`, $pMCMC_{\alpha = 0.05}$ = `r p_act_pl`, $R_{^2}$ = 0.068). We did not capture an effect of parasite load on exploration or boldness (). 

no interwaction between parasites = good
Looking at the experimentally infected fish. When we include parasite load, strong effect on activity, decrease activity. Interaction. And two types parasites (differents modes). Distinct differences between parasites. Unexpected, then explored. More conservative models. Something worth pointing out even if it's not significant. 


```{r}
#| label: fig-fig1
#| fig-cap: Correlation between traits
#| out-width: 100%
#| fig-width: 7
#| fig-height: 8


#Boldness and activity average between trials
dat_E <- read.table("./output/dat_models_E.csv",header=T, sep=",")
dat_C <- read.table("./output/dat_models_C.csv",header=T, sep=",")

#Boldness activity 
p1<-
   ggplot(data=dat_C)+
  geom_point(mapping = aes(x = log_boldness, y = log_activity, color = factor(ID_fish)))+ scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_boldness, y = log_activity, color = factor(ID_fish))) + 
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Boldness_{log_{2}}$"), y = TeX("$Activity_{log_{2}}$"), title = "Uninfected") +
  annotate("text", x = -1.3, y = 2.8, label = TeX(paste0("$r_{b}$ = "," -0.52 ", " 95%CI: -0.87, -0.03")), size =3, color = "darkblue") + 
  annotate("text", x = -1.3, y = 2.4, label = TeX(paste0("$r_{w}$ = ", " 0.18 ", " 95%CI: -0.06, 0.40")), size=3, color = "darkgreen")

p2<-
  ggplot(data=dat_E)+
  geom_point(mapping = aes(x = log_boldness, y = log_activity, color = factor(ID_fish)))+ scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_boldness, y = log_activity, color = factor(ID_fish))) + 
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Boldness_{log_{2}}$"), y = TeX("$Activity_{log_{2}}$"), title = "Infected") +
  annotate("text", x = -1.5, y = 2.8, label = TeX(paste0("$r_{b}$ = ", " -0.43 ", " 95%CI: -0.84, 0.13 ")), size =3, color = "darkblue") + 
  annotate("text", x = -1.5, y = 2.4, label = TeX(paste0("$r_{w}$ = ", " 0.17 ", " 95%CI: -0.07, 0.39")), size=3, color = "darkgreen")
 
 p_1<- plot_grid(
  p1, p2, ncol = 2)

    #Boldness and exploration average between trials
            
  p3<-
 ggplot(data=dat_C)+
  geom_point(mapping = aes(x = log_boldness, y = exploration, color = factor(ID_fish)))+ scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_boldness, y = exploration, color = factor(ID_fish))) + 
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Boldness_{log_{2}}$"), y = TeX("Exploration"), title = "Uninfected") +
  annotate("text", x = -1.3, y = 2.8, label = TeX(paste0("$r_{b}$ = ", " -0.41 ", " 95%CI: -0.83, 0.11 ")), size =3, color = "darkblue") + 
  annotate("text", x = -1.3, y = 2.4, label = TeX(paste0("$r_{w}$ = ", " -0.06 ", " 95%CI: -0.27, 0.17")), size=3, color = "darkgreen")
  

  p4<-
    ggplot(data=dat_E)+
  geom_point(mapping = aes(x = log_boldness, y = exploration, color = factor(ID_fish)))+ scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_boldness, y = exploration, color = factor(ID_fish))) + 
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Boldness_{log_{2}}$"), y = TeX("Exploration"), title = "Infected") +
  annotate("text", x = 1, y = 2.8, label = TeX(paste0("$r_{b}$ = ", " -0.42 ", " 95%CI: -0.85, 0.25 ")), size =3, color = "darkblue") + 
  annotate("text", x = 1, y = 2.4, label = TeX(paste0("$r_{w}$ = ", " -0.12 ", " 95%CI: -0.33, 0.09")), size=3, color = "darkgreen")
    
  
   p_2<- plot_grid(
  p3, p4, ncol = 2)

    
  #Activity and exploration average between trials

    p5<-
 ggplot(data=dat_C)+
  geom_point(mapping = aes(x = log_activity, y = exploration, color = factor(ID_fish)))+ scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_activity, y = exploration, color = factor(ID_fish))) + 
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Activity_{log_{2}}$"), y = TeX("Exploration"), title = "Uninfected") +
  annotate("text", x = -1.3, y = 2.8, label = TeX(paste0("$r_{b}$ = ", " 0.70 ", " 95%CI: 0.37, 0.93")), size =3, color = "darkblue") + 
  annotate("text", x = -1.3, y = 2.4, label = TeX(paste0("$r_{w}$ = ", " 0.19 ", " 95%CI: -0.04, 0.40")), size=3, color = "darkgreen")
  
  p6<-
    ggplot(data=dat_E)+
  geom_point(mapping = aes(x = log_activity, y = exploration, color = factor(ID_fish)))+ scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_activity, y = exploration, color = factor(ID_fish))) + 
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Activity_{log_{2}}$"), y = TeX("Exploration"), title = "Infected") +
  annotate("text", x = -1, y = 2.8, label = TeX(paste0("$r_{b}$ = ", " 0.14 ", " 95%CI: -0.43, 0.66 ")), size =3, color = "darkblue") + 
  annotate("text", x = -1, y = 2.4, label = TeX(paste0("$r_{w}$ = ", " -0.14 ", " 95%CI: -0.35, 0.08")), size=3, color = "darkgreen")
    

  p_3<-plot_grid(
  p5, p6, ncol = 2)

  plot_grid(
  p_1, p_2, p_3,
  labels = "AUTO", ncol = 1)


```

```{r}
#| label: fig-fig2
#| fig-cap: Plotting model
#| out-width: 100%
#| fig-width: 7
#| fig-height: 4

#Create dataframe with estimates and CI

#Extract post sd from model 2 for each traits and treatment
int_b <- as_draws_df(model2, variable = "^b", regex = TRUE)

#intercept for control
int_b_c<-int_b[,grep("logboldness_Intercept", colnames(int_b))]
int_exp_c<-int_b[,grep("exploration_Intercept", colnames(int_b))]
int_act_c<-int_b[,grep("logactivity_Intercept", colnames(int_b))]

#mean estimates for control
int_b_c_num<- as.numeric(unlist(int_b_c))
mean_int_b_c<-mean(int_b_c_num)

int_exp_c_num<- as.numeric(unlist(int_exp_c))
mean_int_exp_c<-mean(int_exp_c_num)

int_act_c_num<- as.numeric(unlist(int_act_c))
mean_int_act_c<-mean(int_act_c_num)

#contrast between intercept C and E
int_b_con<-int_b[,grep("b_logboldness_treatmentE", colnames(int_b))]
int_exp_con<-int_b[,grep("b_exploration_treatmentE", colnames(int_b))]
int_act_con<-int_b[,grep("b_logactivity_treatmentE", colnames(int_b))]

#mean estimates for contrast
int_b_con_num<- as.numeric(unlist(int_b_con))
mean_con_b<-mean(int_b_con_num)

int_exp_con_num<- as.numeric(unlist(int_exp_con))
mean_con_exp<-mean(int_exp_con_num)

int_act_con_num<- as.numeric(unlist(int_act_con))
mean_con_act<-mean(int_act_con_num)

#subtract intercept for C - contrast to get intercept for E
int_b_e<-(int_b_c_num + int_b_con_num)
int_b_e_num<- as.numeric(unlist(int_b_e))
mean_int_b_e<-mean(int_b_e_num)

int_exp_e<-(int_exp_con_num + int_exp_c_num)
int_exp_e_num<- as.numeric(unlist(int_exp_e))
mean_int_exp_e<-mean(int_exp_e_num)

int_act_e<-(int_act_con_num + int_act_c_num)
int_act_e_num<- as.numeric(unlist(int_act_e))
mean_int_act_e<-mean(int_act_e_num)

 
#is E and C significantly different for each trait?
pm_b<-pmcmc(int_b_c_num - int_b_e_num, twotail = TRUE) #significantly different
pm_exp<-pmcmc(int_exp_c_num - int_exp_e_num, twotail = TRUE) #significantly different
pm_act<-pmcmc(int_act_c_num - int_act_e_num, twotail = TRUE) #not significant


#95% IC
#Boldness
  #Control
blb_b_c <- round(quantile(int_b_c_num, c(0.025, 0.975))[1], 3)
bub_b_c <- round(quantile(int_b_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
blb_b_e<- round(quantile(int_b_e, c(0.025, 0.975))[1], 3)
bub_b_e<- round(quantile(int_b_e, c(0.025, 0.975))[2], 3)

#Exploration
  #Control
blb_exp_c <- round(quantile(int_exp_c_num, c(0.025, 0.975))[1], 3)
bub_exp_c <- round(quantile(int_exp_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
blb_exp_e <- round(quantile(int_exp_e, c(0.025, 0.975))[1], 3)
bub_exp_e <- round(quantile(int_exp_e, c(0.025, 0.975))[2], 3)

#Activity
  #Control
blb_act_c <- round(quantile(int_act_c_num, c(0.025, 0.975))[1], 3)
bub_act_c <- round(quantile(int_act_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
blb_act_e <- round(quantile(int_act_e, c(0.025, 0.975))[1], 3)
bub_act_e <- round(quantile(int_act_e, c(0.025, 0.975))[2], 3)

#Create data frame
dat_model<-data.frame(
  trait=c("logboldness","logboldness","exploration","exploration","logactivity","logactivity"),
  treatment=c("Uninfected","Infected","Uninfected","Infected","Uninfected","Infected"), 
  estimate = c(mean_int_b_c,mean_int_b_e,mean_int_exp_c,mean_int_exp_e, mean_int_act_c, mean_int_act_e), 
  Lower_CI = c(blb_b_c, blb_b_e, blb_exp_c, blb_exp_e, blb_act_c, blb_act_e),
  Higher_CI = c(bub_b_c,bub_b_e,bub_exp_c,bub_exp_e,bub_act_c,bub_act_e))


all_data[all_data == 'C'] <- 'Uninfected'
all_data[all_data == 'E'] <- 'Infected'

#plot model2      
all_data$treatment <- factor(all_data$treatment, levels=c("Uninfected", "Infected"))
trt <- as.factor(all_data$treatment)

dat1<-dat_model %>% 
  filter(trait == "logboldness")


#boldness
m1<-
ggplot(all_data, aes(x = trt, y = log_boldness, group = trt, color = trt)) +
geom_violin(aes(), trim = FALSE) +
geom_jitter(aes(colour = trt),shape=16, position=position_jitter(0.1))+
scale_color_manual(labels = c("Uninfected", "Infected"), values = c("lightgreen", "turquoise"))+
geom_errorbar(data = dat1,aes(x = treatment,y = estimate, ymin= Lower_CI, ymax=Higher_CI), width=0.2, linewidth =0.7, color = "black", inherit.aes = FALSE)+
labs(x = (""), 
y = TeX("$Boldness_{log_{2}}$")) +
theme_classic() +
theme(legend.position = "none",
 legend.title = element_blank()) +
geom_segment(aes(x = 1, xend = 2, y = 3.85, yend = 3.85)) +
annotate("text",  x = 1.5, y = 4, label = TeX(paste0("$pMCMC_{\\alpha = 0.05}$ = 0.0005")), size =2.5)


dat2<-dat_model %>% 
  filter(trait == "exploration")
trt <- as.factor(all_data$treatment)

#exploration
m2<-ggplot(all_data, aes(x = trt, y = exploration, group = trt, col = trt)) +
geom_violin(aes(), trim = FALSE) +
geom_jitter(aes(colour = trt),shape=16, position=position_jitter(0.1)) +
scale_color_manual(labels = c("Uninfected", "Infected"), values = c("lightgreen", "turquoise"))+
geom_errorbar(data = dat2,aes(x = treatment,y = estimate, ymin= Lower_CI, ymax=Higher_CI), width=0.2, linewidth = 0.7, color = "black", inherit.aes = FALSE)+
labs(x = "Treatment", 
y = "Exploration") +
theme_classic() +
theme(legend.position = "none",
 legend.title = element_blank()) +
geom_segment(aes(x = 1, xend = 2, y = 3.85, yend = 3.85)) +
annotate("text",  x = 1.5, y = 4, label = TeX(paste0("$pMCMC_{\\alpha = 0.05}$ = 0.0015")), size =2.5)

#activity
dat3<-dat_model %>% 
  filter(trait == "logactivity")

m3<-ggplot(all_data, aes(x = trt, y = log_activity, group = trt, col = trt)) +
geom_violin(aes(), trim = FALSE) +
geom_jitter(aes(colour = trt), shape=16, position=position_jitter(0.1)) +
geom_point(position = position_dodge(width = 0.1))+
scale_color_manual(labels = c("Uninfected", "Infected"), values = c("lightgreen", "turquoise"))+
geom_errorbar(data = dat3,aes(x = treatment,y = estimate, ymin= Lower_CI, ymax=Higher_CI), width=0.2, linewidth =0.7, color = "black", inherit.aes = FALSE)+
labs(x = "", 
y = TeX("$Activity_{log_{2}}$")) +
theme_classic() +
theme(legend.position = "none",
 legend.title = element_blank()) +
geom_segment(aes(x = 1, xend = 2, y = 3.85, yend = 3.85)) +
annotate("text",  x = 1.5, y = 4, label = TeX(paste0("$pMCMC_{\\alpha = 0.05}$ = 0.0666")), size =2.5)

 plot_grid(
  m1,m2,m3,
  labels = "AUTO", ncol = 3)
 
#Extract post sd from model 2 for each traits and treatment
# AT ID LEVEL HERE
#post_sd_2 <- as_draws_df(model2, variable = "^sd", regex = TRUE)
#Control
#post_b_c<-post_sd_C_2[,grep("logboldness", colnames(post_sd_C_2))]
#post_exp_c<-post_sd_C_2[,grep("exploration", colnames(post_sd_C_2))]
#post_act_c<-post_sd_C_2[,grep("logactivity", colnames(post_sd_C_2))]

#Experimental
#post_b_e<-post_sd_E_2[,grep("logboldness", colnames(post_sd_E_2))]
#post_exp_e<-post_sd_E_2[,grep("exploration", colnames(post_sd_E_2))]
#post_act_e<-post_sd_E_2[,grep("logactivity", colnames(post_sd_E_2))]

#unlist the data to be able to use the data as numeric
#Control
#post_b_c_num<- as.numeric(unlist(post_b_c))
#post_exp_c_num<- as.numeric(unlist(post_exp_c))
#post_act_c_num<- as.numeric(unlist(post_act_c))

#Experimental
#post_b_e_num<- as.numeric(unlist(post_b_e))
#post_exp_e_num<- as.numeric(unlist(post_exp_e))
#post_act_e_num<- as.numeric(unlist(post_act_e))

#calculate mean estimate
#Control
#mean_b_c<-mean(post_b_c_num)
#mean_exp_c<-mean(post_exp_c_num)
#mean_act_c<-mean(post_act_c_num)

#Experimental
#mean_b_e<-mean(post_b_e_num)
#mean_exp_e<-mean(post_exp_e_num)
#mean_act_e<-mean(post_act_e_num)

#95% IC
#Boldness
  #Control
#blb_b_c <- round(quantile(post_b_c_num, c(0.025, 0.975))[1], 3)
#bub_b_c <- round(quantile(post_b_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
#blb_b_e<- round(quantile(post_b_e_num, c(0.025, 0.975))[1], 3)
#bub_b_e<- round(quantile(post_b_e_num, c(0.025, 0.975))[2], 3)

#Exploration
  #Control
#blb_exp_c <- round(quantile(post_exp_c_num, c(0.025, 0.975))[1], 3)
#bub_exp_c <- round(quantile(post_exp_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
#blb_exp_e <- round(quantile(post_exp_e_num, c(0.025, 0.975))[1], 3)
#bub_exp_e <- round(quantile(post_exp_e_num, c(0.025, 0.975))[2], 3)

#Activity
  #Control
#blb_act_c <- round(quantile(post_act_c_num, c(0.025, 0.975))[1], 3)
#bub_act_c <- round(quantile(post_act_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
#blb_act_e <- round(quantile(post_act_e_num, c(0.025, 0.975))[1], 3)
#bub_act_e <- round(quantile(post_act_e_num, c(0.025, 0.975))[2], 3)

#create data frame with metrics from posterior distribution from model2
#dat_model2<-data.frame(
  #trait=c("logboldness","logboldness","exploration","exploration","logactivity","logactivity"),
  #treatment=c("uninfected","infected","uninfected","infected","uninfected","infected"), 
  #estimate = c(mean_b_c,mean_b_e,mean_exp_c,mean_exp_e, mean_act_c,mean_act_e), 
  #Lower_CI = c(blb_b_c, blb_b_e, blb_exp_c, blb_exp_e, blb_act_c, blb_act_e),
 # Higher_CI = c(bub_b_c,bub_b_e,bub_exp_c,bub_exp_e,bub_act_c,bub_act_e))

      
#plot model2      
#w1<-ggplot(data = dat_model2) +
#geom_point(mapping = aes(x = treatment, y = estimate, color = trait))
  
#w2<-ggplot(data = all_data) + 
#geom_point(mapping = aes(x = treatment, y = log_activity))

#w3<-ggplot(data = all_data) + 
#geom_point(mapping = aes(x = treatment, y = exploration))

 #plot_grid(
  #w1, w2, w3,
  #labels = "AUTO", ncol = 1)

```

```{r}
#| label: fig-fig3
#| fig-cap: Effect of parasite load
#| out-width: 100%
#| fig-width: 7
#| fig-height: 8

    ggplot(data=dat_parasite)+
  geom_smooth(mapping = aes(x = z_pl, y = log_boldness), color = "red")+
  geom_smooth(mapping = aes(x = z_ces, y = log_boldness), color = "green")+
  geom_smooth(mapping = aes(x = z_bs, y = log_boldness))+
  geom_point(mapping = aes(x = z_pl, y = log_boldness))+
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Boldness_{log_{2}}$"), y = TeX("Parasite load"), title = "")
  #annotate("text", x = 1, y = 2.8, label = TeX(paste0("$r_{b}$ = ", " -0.42 ", " 95%CI: -0.85, 0.25 ")), size =3, color = "darkblue") + 
  #annotate("text", x = 1, y = 2.4, label = TeX(paste0("$r_{w}$ = ", " -0.12 ", " 95%CI: -0.33, 0.09")), size=3, color = "darkgreen")

ggplot(data=dat_parasite)+
  geom_smooth(mapping = aes(x = z_pl, y = log_activity), color = "red")+
  geom_smooth(mapping = aes(x = z_ces, y = log_activity), color = "green")+
  geom_smooth(mapping = aes(x = z_bs, y = log_activity))+
  geom_point(mapping = aes(x = z_pl, y = log_activity))+
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("Parasite load"), y = TeX("$Activity_{log_{2}}$ load"), title = "")
    
ggplot(data=dat_parasite)+
  geom_smooth(mapping = aes(x = z_pl, y = exploration), color = "red")+
  geom_smooth(mapping = aes(x = z_ces, y = exploration), color = "green")+
  geom_smooth(mapping = aes(x = z_bs, y = exploration))+
  geom_point(mapping = aes(x = z_pl, y = exploration))+
   theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("Parasite load"), y = TeX("Exploration"), title = "")
    

```


```{r}
#| label: tbl-tab1
#| tbl-cap: Repeatbility estimates for traits
#| 
tab1 <- data.frame(Trait = c("Boldness (log)", "Exploration","Activity (log)"), 
                "Group C" = c(mean(R_C_boldness[,1]), mean(R_C_exploration[,1]), mean(R_C_activity[,1])), 
                  "2.5% CI (C)" = c((R_Blb_bold_C),(R_Blb_exp_C), (R_Blb_act_C)),
              "97.5% CI (C)" = c((R_Bub_bold_C), (R_Bub_exp_C),(R_Bub_act_C)),
                "Group E" = c(mean(R_E_boldness[,1]), mean(R_E_exploration[,1]), mean(R_E_activity[,1])),
              "2.5% CI (E)" = c((R_Blb_bold_E), (R_Blb_exp_E), (R_Blb_act_E)), "97.5% CI (E)" = c((R_Bub_bold_E), (R_Bub_exp_E), (R_Bub_act_E)), check.names = FALSE)

gt(tab1) 

```
