---
format:
  docx: 
    reference-doc: "./bib/template.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
crossref:  
  fig-title: Fig.    # (default is "Figure")
  tbl-title: Table   # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.   # (default is "Table")
editor_options: 
  chunk_output_type: console
---

# Results

```{r}
#| label: load_packages
#| output: false
#| warning: false

    source("./R/func.R")
    pacman::p_load(tidyverse, brms, glmmTMB, gt, posterior)
    options(digits = 3)
```

```{r}
#| label: load_data
#| output: false
#| warning: false

############################
# Import processed data
#############################
  all_data <- read.table("./output/all_data_p.csv",header=T, sep=",")
  all_data

  
############################
# Parasite count
#############################
### Blackspots distribution
hist(all_data$BS_post_tot)

# Blackspots info
BS_min<-min(all_data$BS_post_tot)
BS_max<-max(all_data$BS_post_tot)
BS_median<-median(all_data$BS_post_tot)

### Cestodes distribution
hist(all_data$P04_alive)

# Cestodes info
cestode_min<-min(all_data$P04_alive)
cestode_max<-max(all_data$P04_alive)
cestode_median<-median(all_data$P04_alive)
mean(all_data$P04_alive)

### Nematodes distribution
hist(all_data$P013_alive)

# Nematodes info
nematode_min<-min(all_data$P013_alive)
nematode_max<-max(all_data$P013_alive)

### Looking at BS gained after infection
# Create new columns in the dataset
all_data$BS_gain<- all_data$BS_post_tot - all_data$BS_pre

# BS gain distribution
hist(all_data$BS_gain)

# BS gain info
gain_min<-min(all_data$BS_gain) ### miscount, some fish have less BS after infection
gain_max<-max(all_data$BS_gain)
gain_median<-median(all_data$BS_gain)
gain_mean<-mean(all_data$BS_gain)

############################
# Load model
############################

  model1 <- readRDS(file = "./output/models/model1.rds")
  model2 <- readRDS(file = "./output/models/model2.rds")
  # Calculate repeatability
    post_sd <- as_draws_df(model1, variable = "^sd", regex = TRUE)
    post_sd_C <- post_sd[,grepl("C", colnames(post_sd))]
    post_sd_E <- post_sd[,grepl("E", colnames(post_sd))]
    post_sd_cage <- post_sd[,grepl("cage", colnames(post_sd))]
    post_sd_sig <- as_draws_df(model1, variable = "^sigma", regex = TRUE)
    
  # Repeatability for the traits across treatment
source("./R/func.R")
    #Boldness
       R_boldness <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logboldness")
       R_Blb_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[1], 2)
       R_Bub_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[2], 2)
      hist(R_boldness[,1])
      R_bold_mean<-mean(R_boldness[,1])
      
      #Exploration
       R_explore <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "exploration")
       R_Blb_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[1], 2)
       R_Bub_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[2], 2)
       hist(R_explore[,1])
       R_exp_mean<-mean(R_explore[,1])
      
       #Activity
       R_activity <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logactivity")
       R_Blb_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[1], 2)
       R_Bub_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[2], 2)
       hist(R_activity[,1])
       R_act_mean<-mean(R_activity[,1])
      
  # Compare whether repeatability is different between exploratory and boldness
      R_contrast <- R_explore - R_boldness
  
  
      
# Repeatability for the traits between treatment
source("./R/reap_each.R")

post_sd <- as_draws_df(model1, variable = "^sd", regex = TRUE)
post_sd_C <- post_sd[,grepl("C", colnames(post_sd))]
post_sd_E <- post_sd[,grepl("E", colnames(post_sd))]
post_sd_cage <- post_sd[,grepl("cage", colnames(post_sd))]
post_sd_sig <- as_draws_df(model2, variable = "^b_sigma", regex = TRUE)

post_sd_C_exp<-exp(post_sd_C)
post_sd_E_exp<-exp(post_sd_E)

# Group E
#Boldness 
R_boldness_2 <- rep_each(post_sd_E_exp, post_sd_cage, post_sd_sig, trait = "logboldness")
R_Blb_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[1], 2)
R_Bub_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[2], 2)
hist(R_boldness[,1])
R_bold_mean<-mean(R_boldness[,1])

#Exploration
R_explore <- repeatability(post_sd_E, post_sd_cage, post_sd_sig, trait = "exploration")
R_Blb_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[1], 2)
R_Bub_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[2], 2)
hist(R_explore[,1])
R_exp_mean<-mean(R_explore[,1])

#Activity
R_activity <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logactivity")
R_Blb_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[1], 2)
R_Bub_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[2], 2)
hist(R_activity[,1])
R_act_mean<-mean(R_activity[,1])

#Group C

#Boldness
R_boldness <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logboldness")
R_Blb_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[1], 2)
R_Bub_bold <- round(quantile(R_boldness[,1], c(0.025, 0.975))[2], 2)
hist(R_boldness[,1])
R_bold_mean<-mean(R_boldness[,1])

#Exploration
R_explore <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "exploration")
R_Blb_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[1], 2)
R_Bub_exp <- round(quantile(R_explore[,1], c(0.025, 0.975))[2], 2)
hist(R_explore[,1])
R_exp_mean<-mean(R_explore[,1])

#Activity
R_activity <- repeatability(post_sd_C, post_sd_E, post_sd_cage, post_sd_sig, trait = "logactivity")
R_Blb_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[1], 2)
R_Bub_act <- round(quantile(R_activity[,1], c(0.025, 0.975))[2], 2)
hist(R_activity[,1])
R_act_mean<-mean(R_activity[,1])
    
    
    
    
```

The caging experiment successfully infected our treatment fish. Control fish that stayed in the laboratory had no alive parasite, which indicate that the praziquantel treatment was effective. The two most abundant species found in the experimentally infected fish were trematodes causing the blackspot disease (Trematoda: *Apophallus sp.* and *Uvulifer sp.*; min-max: `r BS_min`- `r BS_max`; median: `r BS_median`) and the bass tapeworm (Cestoda: *Proteocephalus ambloplites*; min-max: `r cestode_min` - `r cestode_max` ; median: `r cestode_median`). The most abundant species of trematode causing blackspots was *Apophallus sp*. (Binning, Lanthier, unpublished data), but *Uvulifer sp.* was found more frequently inside the muscles (MG, personal observations).Experimentally fish gained in mean `r gain_mean` blackspots, and were found on the fines, body, gills and inside the muscles. Bass tapeworm were mostly found in the liver, stomach and digestive tract, occasionally around the spleen (parasite count: 9), and rarely on the gills (parasite count: 3) or the heart (parasite count: 2). Unknown nematode species were found rarely in the body cavity (alive parasite count: 4).

The average repeatbility of each traits across trial were `r round(R_exp_mean)` (95% CI: `r R_Blb_bold` to `r R_Bub_bold`) for boldness; `r round(R_exp_mean)`(95% CI: `r R_Blb_exp` to `r R_Bub_exp`) for exploration; and `r round(R_act_mean)`(95% CI: `r R_Blb_act` to `r R_Bub_act`) for activity (tab1).

#### *Boldness*

```{r}
#| label: fig-fig1
#| fig-cap: Repeatbility of behavioural traits
#| 
hist(R_boldness[,1])
```

```{r, tbl-tab1}
#| label: tbl-tab1
#| tbl-cap: Repeatbility estimates for traits
tab1 <- data.frame(Trait = c("log_Boldness", "Exploration","log_Activity"), 
"Group E" =  c(mean(R_bold_E[,1]), mean(R_exp_E[,1]), mean(R_act_E[,1])), "Group C" = c(mean(R_bold_C[,1]), mean(R_exp_C[,1]), mean(R_act_C[,1])),
"2.5% CI" = c(round(R_Blb_bold, 2), round(R_Blb_exp, 2), round(R_Blb_act), 2), "97.5% CI" = c(round(R_Bub_bold, 2), round(R_Bub_exp, 2), round(R_Bub_act), 2), check.names = FALSE)

gt(tab1) %>% cols_align(align="center")
gt(tab1) %>% tab_header(
    title = "Repeatability for each personality trait")
gt(tab1) %>% tab_spanner(
    label = "Treatment",
    columns = c("Group E","Group C")
  )
```
