---
format:
  docx: 
    reference-doc: "./bib/template.docx"
    fig-width: 7
    fig-height: 8
execute:
  echo: false
  error: false
  cache: false
  warning: false
crossref:  
  fig-title: Figure    # (default is "Figure")
  tbl-title: Table   # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.   # (default is "Table")
editor_options: 
  chunk_output_type: console
---

# Results

```{r}
#| label: load_packages
#| output: false
#| warning: false

    source("./R/func.R")
    pacman::p_load(tidyverse, brms, glmmTMB, gt, latex2exp, posterior, gt, glue, dplyr,magrittr, ggplot2, cowplot)
    options(digits = 3, scipen = 2)
    
```

```{r}
#| label: load_data
#| output: false
#| warning: false

############################
# Import processed data
#############################
  all_data <- read.table("./output/all_data_p.csv",header=T, sep=",")
  
############################
# Parasite count
#############################
### Blackspots distribution
  hist(all_data$BS_post_tot)

# Blackspots info
  BS_min<-min(all_data$BS_post_tot)
  BS_max<-max(all_data$BS_post_tot)
  BS_median<-median(all_data$BS_post_tot)

### Cestodes distribution
  hist(all_data$P04_alive)

# Cestodes info
  cestode_min<-min(all_data$P04_alive)
  cestode_max<-max(all_data$P04_alive)
  cestode_median<-median(all_data$P04_alive)
  mean(all_data$P04_alive)

### Nematodes distribution
  hist(all_data$P013_alive)

# Nematodes info
  nematode_min<-min(all_data$P013_alive)
  nematode_max<-max(all_data$P013_alive)

### Looking at BS gained after infection
# Create new columns in the dataset
  all_data$BS_gain<- all_data$BS_post_tot - all_data$BS_pre

# BS gain distribution
  hist(all_data$BS_gain)

# BS gain info
  gain_min<-min(all_data$BS_gain) ### miscount, some fish have less BS after infection
  gain_max<-max(all_data$BS_gain)
  gain_median<-median(all_data$BS_gain)
  gain_mean<-mean(all_data$BS_gain)

############################
# Load model
############################

  model1 <- readRDS(file = "./output/models/model1.rds")
  model1.2 <- readRDS(file = "./output/models/model1.2.rds")
  model2 <- readRDS(file = "./output/models/model2.rds")
  model2.2 <- readRDS(file = "./output/models/model2.2.rds")

    
############################
# Repeatability C vs E
############################

         post_sd_2 <- as_draws_df(model2, variable = "^sd", regex = TRUE)
       post_sd_C_2 <- post_sd_2[,grepl("C", colnames(post_sd_2))] #ID control
       post_sd_E_2 <- post_sd_2[,grepl("E", colnames(post_sd_2))] #ID experimental
    post_sd_cage_2 <- post_sd_2[,grepl("cage", colnames(post_sd_2))]
     post_sd_sig_2 <- as_draws_df(model2, variable = "^b_sigma", regex = TRUE)
     post_sd_sig_C_2 <- exp(post_sd_sig_2[,grepl("C", colnames(post_sd_sig_2))]) #ID control
       post_sd_sig_E_2 <- exp(post_sd_sig_2[,grepl("E", colnames(post_sd_sig_2))]) #ID experimental

############################
##     CONTROL GROUP
############################

#Boldness for control group
  fish_c_b <- post_sd_C_2[,grep("logboldness", colnames(post_sd_C_2))]^2
  cage_c_b <- post_sd_cage_2[ ,grep("logboldness", colnames(post_sd_cage_2))]^2
   res_c_b <- post_sd_sig_C_2[,grep("b_sigma_logboldness_treatmentC", colnames(post_sd_sig_C_2))]^2

  R_C_boldness <-   fish_c_b / (fish_c_b + cage_c_b + res_c_b)

#verification
 0.40^2 / (0.15^2 + 0.40^2 + exp(-0.14)^2)
 
  hist(R_C_boldness[,1])
  R_C_bold <- mean(R_C_boldness[,1])
  R_Blb_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_C <- round(quantile(R_C_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for control group
  fish_c_ex <- post_sd_C_2[,grep("exploration", colnames(post_sd_C_2))]^2
  cage_c_ex <- post_sd_cage_2[ ,grep("exploration", colnames(post_sd_cage_2))]^2
   res_c_ex <- post_sd_sig_C_2[,grep("b_sigma_exploration_treatmentC", colnames(post_sd_sig_C_2))]^2

  R_C_exploration <-   fish_c_ex / (fish_c_ex + cage_c_ex + res_c_ex)
  
#verification
  0.57^2 / (exp(-0.11)^2 + 0.57^2 + 0.16^2) #same number

  hist(R_C_exploration[,1])
  mean(R_C_exploration[,1])
  R_Blb_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_C <- round(quantile(R_C_exploration[,1], c(0.025, 0.975))[2], 3)

#activity for control group
  fish_c_ac <- post_sd_C_2[,grep("logactivity", colnames(post_sd_C_2))]^2
  cage_c_ac <- post_sd_cage_2[ ,grep("logactivity", colnames(post_sd_cage_2))]^2
  res_c_ac <- post_sd_sig_C_2[,grep("b_sigma_logactivity_treatmentC", colnames(post_sd_sig_C_2))]^2

  R_C_activity <-   fish_c_ac / (fish_c_ac + cage_c_ac + res_c_ac)
  
#verification
  0.64^2 / (exp(-0.15)^2 + 0.64^2 + 0.11^2) 

  hist(R_C_activity[,1])
  mean(R_C_activity[,1])
  R_Blb_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_C <- round(quantile(R_C_activity[,1], c(0.025, 0.975))[2], 3)

############################
# EXPERIMENTAL GROUP
############################

#Boldness for experimental group
  fish_e_b <- post_sd_E_2[,grep("logboldness", colnames(post_sd_E_2))]^2
  cage_e_b <- post_sd_cage_2[ ,grep("logboldness", colnames(post_sd_cage_2))]^2
  res_e_b <- post_sd_sig_E_2[,grep("b_sigma_logboldness_treatmentE", colnames(post_sd_sig_E_2))]^2

  R_E_boldness <-   fish_e_b / (fish_e_b + cage_e_b + res_e_b)
  
#verification
  0.42^2 / (exp(-0.11)^2 + 0.42^2 + 0.15^2)

  hist(R_E_boldness[,1])
  mean(R_E_boldness[,1])
  R_Blb_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[1], 3)
  R_Bub_bold_E <- round(quantile(R_E_boldness[,1], c(0.025, 0.975))[2], 3)

#exploration for experimental group
   fish_e_ex <- post_sd_E_2[,grep("exploration", colnames(post_sd_E_2))]^2
  cage_e_ex <- post_sd_cage_2[ ,grep("exploration", colnames(post_sd_cage_2))]^2
  res_e_ex <- post_sd_sig_E_2[,grep("b_sigma_exploration_treatmentE", colnames(post_sd_sig_E_2))]^2

  R_E_exploration <-   fish_e_ex / (fish_e_ex + cage_e_ex + res_e_ex)
  
#verification
  0.38^2 / (exp(-0.28)^2 + 0.38^2 + 0.16^2) 

  hist(R_E_exploration[,1])
  mean(R_E_exploration[,1])
  R_Blb_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[1], 3)
  R_Bub_exp_E <- round(quantile(R_E_exploration[,1], c(0.025, 0.975))[2], 3)

#activity for experimental group
  fish_e_ac <- post_sd_E_2[,grep("logactivity", colnames(post_sd_E_2))]^2
  cage_e_ac <- post_sd_cage_2[ ,grep("logactivity", colnames(post_sd_cage_2))]^2
  res_e_ac <- post_sd_sig_E_2[,grep("b_sigma_logactivity_treatmentE", colnames(post_sd_sig_E_2))]^2

  R_E_activity <-   fish_e_ac / (fish_e_ac + cage_e_ac + res_e_ac)

#verification
  0.51^2 / (exp(-0.26)^2 + 0.51^2 + 0.11^2) 
  
  hist(R_E_activity[,1])
  mean(R_E_activity[,1])
  R_Blb_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[1], 3)
  R_Bub_act_E <- round(quantile(R_E_activity[,1], c(0.025, 0.975))[2], 3)

#############################
# Overall Repeatability
#############################

  # Boldness
   R_bold  <-  overall_repeatability(post_sd_C_2, post_sd_E_2, post_sd_cage_2, post_sd_sig_C_2, post_sd_sig_E_2, trait = "logboldness")
  
        R_bold_mean <- mean(R_bold)
        R_Blb_bold <- round(quantile(R_bold, c(0.025, 0.975))[1], 2)
        R_Bub_bold <- round(quantile(R_bold, c(0.025, 0.975))[2], 2)
        
  #Exploration
  R_exp  <-  overall_repeatability(post_sd_C_2, post_sd_E_2, post_sd_cage_2, post_sd_sig_C_2, post_sd_sig_E_2, trait = "exploration")
  
      R_exp_mean<-mean(R_exp)
       R_Blb_exp <- round(quantile(R_exp, c(0.025, 0.975))[1], 2)
       R_Bub_exp <- round(quantile(R_exp, c(0.025, 0.975))[2], 2)
       
  #Activity
  R_act  <-  overall_repeatability(post_sd_C_2, post_sd_E_2, post_sd_cage_2, post_sd_sig_C_2, post_sd_sig_E_2, trait = "logactivity")
  
  R_act_mean<-mean(R_act)
       R_Blb_act <- round(quantile(R_act, c(0.025, 0.975))[1], 2)
       R_Bub_act <- round(quantile(R_act, c(0.025, 0.975))[2], 2)

#################################
# Compare R in E and C treatments
#################################

#Is the repeatability different before and after treatment ? 
  
  #Boldness
  p_value_bold<-pmcmc((R_C_boldness[,1]) - (R_E_boldness[,1])) # Not different
  # That makes sense given:
  par(mfrow = c(1,2))
  hist(R_E_boldness[,1])
  hist(R_C_boldness[,1])
  
  #Exploration
  p_value_exp<-pmcmc((R_C_exploration[,1]) - (R_E_exploration[,1])) #not different
  
  # Histograms
  hist(R_E_exploration[,1])
  hist(R_C_exploration[,1])
  
  #Activity
  p_value_act<-pmcmc((R_C_activity[,1]) - (R_E_activity[,1])) #not different
  
   # Histograms
  hist(R_E_activity[,1])
  hist(R_C_activity[,1])
  
  
#Is the repeatability different from 5?

#Boldness control
  p_value_bold_C<-pmcmc(R_C_boldness[,1]*100, null = 5, twotail = FALSE)#not significative
#Boldness experimental
  p_value_bold_E<-pmcmc(R_E_boldness[,1]*100, null = 5, twotail = FALSE)#not significative
#Average boldness
  p_value_bold_a<-pmcmc(R_bold*100, null = 5, twotail = FALSE)#not significative but really close
  
#Exploration control
  p_value_exp_C<-pmcmc(R_C_exploration[,1]*100, null = 5, twotail = FALSE)#significative
  
  hist(R_C_exploration[,1])
  hist(R_E_exploration[,1])
#Exploration experimental
  p_value_exp_E<-pmcmc(R_E_exploration[,1]*100, null = 5, twotail = FALSE)#not significative
#Average exploration
  p_value_exp_a<-pmcmc(R_exp*100, null = 5, twotail = FALSE)#significative

#Activity control
  p_value_act_C<-pmcmc(R_C_activity[,1]*100, null = 5, twotail = FALSE)##significative
  hist(R_C_activity[,1])
#Activity experimental
  p_value_act_E<-pmcmc(R_E_activity[,1]*100, null = 5, twotail = FALSE)#significative
#Activity average
  p_value_act_a<-pmcmc(R_act*100, null = 5,twotail = FALSE) #significative
  
  
#################################
# Behavioural Syndromes
#################################
  
# Extract correlations from model
  post_cor  <- as_draws_df(model2, variable = "^cor", regex= TRUE)
  head(post_cor)

# Extract the C and E groups separately
  cor_bold_treatC <-   post_cor[,grep("treatmentC__[a-z]*_treatmentC", colnames(post_cor))]
  cor_bold_treatE <-   post_cor[,grep("treatmentE__[a-z]*_treatmentE", colnames(post_cor))]

# See if syndromes differ in C and E
  #how to you know if they are different? CI overlap?
  
  #Boldness and activity
  bsyn_b_act_C <- data.frame(cor_bold_treatC[,1]); mean(bsyn_b_act_C[,1]); quantile(bsyn_b_act_C[,1], c(0.025, 0.975))
  
  bsyn_b_act_E <- data.frame(cor_bold_treatE[,1]); mean(bsyn_b_act_E[,1]); quantile(bsyn_b_act_E[,1], c(0.025, 0.975))
  
  pmcmc_b_act_E<-pmcmc(bsyn_b_act_E[,1], twotail = TRUE)
  pmcmc_b_act_C<-pmcmc(bsyn_b_act_C[,1], twotail = TRUE)
  
  #is the difference significant
   pmcmc_b_act<-pmcmc(bsyn_b_act_C[,1] - bsyn_b_act_E[,1], twotail = TRUE) #no
  
  #Boldness and exploration
  bsyn_b_exp_C <- data.frame(cor_bold_treatC[,2]); mean(bsyn_b_exp_C[,1]); quantile(bsyn_b_exp_C[,1], c(0.025, 0.975))
  
  bsyn_b_exp_E <- data.frame(cor_bold_treatE[,2]); mean(bsyn_b_exp_E[,1]); quantile(bsyn_b_exp_E[,1], c(0.025, 0.975))
  
  #is the difference significant
  pmcmc_b_exp<-pmcmc(bsyn_b_exp_C[,1] - bsyn_b_exp_E[,1], twotail = TRUE) #no
  
  #Activity and exploration
  bsyn_act_exp_C <- data.frame(cor_bold_treatC[,3]); mean(bsyn_act_exp_C[,1]); quantile(bsyn_act_exp_C[,1], c(0.025, 0.975))
  
  pmcmc_act_exp_C<- pmcmc(bsyn_act_exp_C[,1], twotail = TRUE) #significant
  
  bsyn_act_exp_E <- data.frame(cor_bold_treatE[,3]); mean(bsyn_act_exp_E[,1]); quantile(bsyn_act_exp_E[,1], c(0.025, 0.975))  
  
   pmcmc_act_exp_E<- pmcmc(bsyn_act_exp_E[,1], twotail = TRUE) #not significant

  #is the difference significant
 pmcmc_act_exp<- pmcmc(bsyn_act_exp_C[,1] - bsyn_act_exp_E[,1], twotail = TRUE) #no
  
# Overall syndrome
  # Take average of the two treatments
    bsyn_b_act   <- cbind(bsyn_b_act_C[,1], bsyn_b_act_E[,1]); mean(rowMeans(bsyn_b_act)); quantile(rowMeans(bsyn_b_act), c(0.025, 0.975))

  # Pool the two MCMC chains from the treatments into a giant vector 32,000 rows (2*16,000)
    #Boldness and activity
bsyn_b_act2  <- rbind(c(bsyn_b_act_C[,1], bsyn_b_act_E[,1]))
mean(bsyn_b_act2)
q_b_act<-quantile(bsyn_b_act2, c(0.025, 0.975))
    
    #Boldness and exploration
bsyn_b_exp  <- rbind(c(bsyn_b_exp_C[,1], bsyn_b_exp_E[,1]))
mean(bsyn_b_exp)
q_b_exp<-quantile(bsyn_b_exp, c(0.025, 0.975))
    
    #Activity and exploration
bsyn_act_exp  <- rbind(c(bsyn_act_exp_C[,1], bsyn_act_exp_E[,1]))
mean(bsyn_act_exp)
q_act_exp<-quantile(bsyn_act_exp, c(0.025, 0.975))
    
#Values in model 1.2 for logactivity-boldness
    #estimate = -0.48
    #CI = -0.93, 0.18 ##pool is closest to model 1.2

    
```
### Methods
#### *Statistical analysis*

All statistical analyses were performed with the software R (version 4.2.2). Adjusted fish mass was calculated as the fish mass minus parasite mass (Lagrue and Poulin, 2015). Parasite mass was estimated with the mean mass of 20 parasites (Vic, in prep). For bass tapeworm, adult average mass was 0.003g and larval form was 0.0008g. We decided to exclude nematodes since the mass varies grandly between individuals and is found rarely in our fish. Blackspots mass was considered too small to be subtracted from total mass ($10^{-7}g$). Body condition was calculated with the Fulton index ($mass/length^3$) (Jakob, 1996) using the adjusted fish mass for the 2 measures of body condition after the experimental infection (we assume there is no parasite before the experimental infection). We used standard length of the fish in centimeters.

Exploration was distributed normally. Activity and boldness were log-transformed to impose normality. All variable were z-scaled. We fitted our models with a Bayesian statistical inference using 4 chains with an iteration of 6000 and a warm up of 2000. We visually inspected the MCMC sampling to see if the sampling ...(?) 

To test if we find evidence of personality and behavioural syndromes between traits, we built a model with the personality traits as response variables, treatment (uninfected vs infected) as a fixed effect, fish ID and cage number as random effects. Model 1 had tank effect as a fixed factor compared to Model 2. We compared the models using the loo package. Model 2 was better fitted (elpd_diff:-3.6 ; se_diff: 1.7) than model 1 and we decided not to include tank effect in our models. Repeatability (R) was calculated using the squared standard deviation for fish ID divided by the squared standard deviation for fish ID, cage and sigma from model 2 for each treatment group and for the average across groups. To estimate if repeatability was different from 0, we choose 0.05 as a threshold since the values can't be 0 in the distribution. Correlation between traits were extracted from model 2 to determine if there was a behavioural syndrome between traits. To measure the average correlation for each group, we pooled the two MCMC chains for both group together.

To test if the experimental infection had an effect on personality, we sublet the data set according to treatment. We used our data set for the experimentally infected group in model 3 and 4 to see if parasite load had a significant effect on the traits responses. Parasite load was included as a fixed factor; fish ID and cage were random factors. Model 3 assume than parasite load effect is linear, so we included parasite $load^2$ as a fixed factor in model 4. We compared model 3 and 4 using the loo method (should we do that?). We fitted model 5 with ID and cage as random effects for our uninfected group. Finally, Model 6 used body condition as the response variable … 

### Results
#### *Experimental infection*

The caging experiment successfully infected our fish. Control fish that stayed in the laboratory had no alive parasite, which indicate that the praziquantel treatment was effective. The two most abundant species found in the experimentally infected fish were trematodes causing the blackspot disease (Trematoda: *Apophallus sp.* and *Uvulifer sp.*; min-max: `r BS_min`- `r BS_max`; median: `r BS_median`) and the bass tapeworm (Cestoda: *Proteocephalus ambloplites*; min-max: `r cestode_min` - `r cestode_max` ; median: `r cestode_median`). The most abundant species of trematode causing blackspots was *Apophallus sp*. (Binning, Lanthier, unpublished data), but *Uvulifer sp.* was found more frequently inside the muscles (MG, personal observations).Experimentally fish gained in mean `r gain_mean` blackspots, and were found on the fines, body, gills and inside the muscles. Bass tapeworm were mostly found in the liver, stomach and digestive tract, occasionally around the spleen (parasite count: 9), and rarely on the gills (parasite count: 3) or the heart (parasite count: 2). Unknown nematode species were found rarely in the body cavity (alive parasite count: 4).

#### *Evidence of personality and behavioural syndromes*

Exploration and activity were repeatable across trials (Exploration: R = `r R_exp_mean`, 95% CI = `r R_Blb_exp`, `r R_Bub_exp`, $pMCMC_{\alpha = 0.05}$ = `r p_value_exp_a`; Activity: R = `r R_act_mean`, 95% CI = `r R_Blb_act`, `r R_Bub_act`, $pMCMC_{\alpha = 0.05}$ = `r p_value_act_a`), but boldness was not significantly repeatable (Boldness: R = `r R_bold_mean`, 95% CI = `r R_Blb_bold`, `r R_Bub_bold`, $pMCMC_{\alpha = 0.05}$ = `r p_value_bold_a`). We did not observe among-individual variation to be higher in the uninfected vs experimentally infected group (@tbl-tab1). Repeatability did not differ between treatment for boldness ($pMCMC_{\alpha = 0.05}$ = `r p_value_bold`), exploration ($pMCMC_{\alpha = 0.05}$ = `r p_value_exp`) and activity ($pMCMC_{\alpha = 0.05}$ = `r p_value_act`).We found evidence of behavioural syndromes between boldness and activity (cor = `r mean(bsyn_b_act2)`, 95% CI = `r q_b_act`); boldness and exploration (cor = `r mean(bsyn_b_exp)`, 95% CI = `r q_b_exp`), and between activity and exploration (cor = `r mean(bsyn_act_exp)`, 95% CI = `r q_act_exp`)  The correlation did not differ between the uninfected and experimentally infected group for these syndromes (Boldness-Activity: $pMCMC_{\alpha = 0.05}$ =  `r pmcmc_b_act`; Boldness-Exploration: $pMCMC_{\alpha = 0.05}$ =  `r pmcmc_b_exp`; Activity-Exploration: $pMCMC_{\alpha = 0.05}$ =  `r pmcmc_act_exp`).



```{r}
#| echo: false
#| include: false

summary(model2)
summary(model1)
```

#### *Effect of parasite*

#### *Behavioural syndromes*

```{r}
#| label: fig-fig1
#| fig-cap: Correlation between traits
#| out-width: 100%

#Boldness and activity average between trials
      
plot_names <- c('C' = "Uninfected",
                'E' = "Infected")
plot_names2 <- c('C' = "",
                'E' = "")

  dat_text <- data.frame(
  label = c("rb = -0.52, 95%CI = -0.87, -0.03\ 
  rw = 0.18, 95%CI =  -0.06, 0.40", 
  "rb = -0.43, 95%CI = -0.84, 0.13\
  rw = 0.17, 95%CI = -0.07, 0.39"),
  treatment   = c("C","E")
)
  
p1<-
  ggplot(data=all_data)+
  geom_point(mapping = aes(x = log_boldness, y = log_activity, color = factor(ID_fish)))+ scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_boldness, y = log_activity, color = factor(ID_fish))) + 
    facet_wrap(~ treatment, labeller = as_labeller(plot_names)) + theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(legend.position="none") + labs(x = TeX("$Boldness_{log_{2}}$"), y = TeX("$Activity_{log_{2}}$"), title = "") + geom_text(
  data    = dat_text,
  mapping = aes(x = -1, y = 3, label = label, group = NULL))
  #  annotate("text", x = -1.5, y = 2.6, label = TeX(paste0("$r_{b}$ = ", " -0.48 ", " 95%CI: -0.86, 0.07 ")), size =2.5, color = "darkblue") + 
   # annotate("text", x = -1.5, y = 2.2, label = TeX(paste0("$r_{w}$ = ", " 0.22 ", " 95%CI: 0.06, 0.36")), size=2.5, color = "darkgreen")


    #Boldness and exploration average between trials
  dat_text2 <- data.frame(
  label = c("rb = -0.41, 95%CI =  -0.83, 0.11\
  rw = -0.06, 95%CI = -0.27, 0.17 ", 
  "rb = -0.42, 95%CI = -0.85, 0.25\
  rw = -0.12, 95%CI =  -0.33, 0.09"),
  treatment   = c("C","E")
)
            
  p2<-
  ggplot(data=all_data)+
  geom_point(mapping = aes(x = log_boldness, y = exploration, color = factor(ID_fish))) +
    scale_color_viridis_d(option = "mako") +
  geom_line(mapping = aes(x = log_boldness, y = exploration, color = factor(ID_fish))) + 
    facet_wrap(~ treatment, labeller = as_labeller(plot_names))+ theme_classic() + 
    theme(strip.background = element_rect(fill = "white", colour = "white"))+
    theme(legend.position="none") + labs(x = TeX("$Boldness_{log_{2}}$"), y = "Exploration")+
  geom_text(
  data    = dat_text2,
  mapping = aes(x = -1, y = 3, label = label, group = NULL))

    #annotate("text", x = 1, y = 2.6, label = TeX(paste0("$r_{b}$ = ", " -0.42 ", " 95%CI: -0.84, 0.18 ")), size =2.5, color="darkblue") + 
   # annotate("text", x = 1, y = 2.2, label = TeX(paste0("$r_{w}$ = ", " -0.06 ", " 95%CI: -0.21, 0.09")), size=2.5, color="darkgreen")
  
   
    #Activity and exploration average between trials
  expression_1<- expression(x[3] ~ variable ~ label)
dat_text3 <- data.frame(
  label = (r = "= 0.70, 95%CI =  0.37, 0.93\
  rw = 0.19, 95%CI = -0.04, 0.40"
  "rb = 0.14, 95%CI = -0.43, 0.66\,
  rw = -0.14, 95%CI = -0.35, 0.08"),
  treatment   = c("C","E")
)

  p3 <- 
  ggplot(data=all_data)+
  geom_point(mapping = aes(x = log_activity, y = exploration, color = factor(ID_fish))) +
  scale_color_viridis_d(option = "mako") + theme_classic() +
  geom_line(mapping = aes(x = log_activity, y = exploration, color = factor(ID_fish) )) +
    facet_wrap(~ treatment, labeller = as_labeller(plot_names)) + theme_classic() +
    theme(strip.background = element_rect(fill = "white", colour = "white")) +
    theme(axis.title = element_text(face = "bold"),
         legend.position="none" ) + labs(x = TeX("$Activity_{log_{2}}$"), y = "Exploration") +
  geom_text(
  data    = dat_text3,
  mapping = aes(x = -1, y = 3, label = label, group = NULL),
)
  

  plot_grid(
  p1, p2, p3,
  labels = "AUTO", ncol = 1)
  
   
   # annotate("text", x = -1.5, y = 2.6, label = TeX(paste0("$r_{b}$ = ", " 0.42 ", " 95%CI: -0.34, 0.91")), size =2.5, color = "darkblue") + 
   # annotate("text", x = -1.5, y = 2.2, label = TeX(paste0("$r_{w}$ = ", " -0.02 ", " 95%CI: -0.17, 0.13")), size=2.5, color = "darkgreen")
  

```

```{r}
#| label: fig-fig2
#| fig-cap: Plotting model
#| out-width: 100%


#Create dataframe with estimates and CI

#Extract post sd from model 2 for each traits and treatment
int_b <- as_draws_df(model2, variable = "^b", regex = TRUE)

#intercept for control
int_b_c<-int_b[,grep("logboldness_Intercept", colnames(int_b))]
int_exp_c<-int_b[,grep("exploration_Intercept", colnames(int_b))]
int_act_c<-int_b[,grep("logactivity_Intercept", colnames(int_b))]

#mean estimates for control
int_b_c_num<- as.numeric(unlist(int_b_c))
mean_int_b_c<-mean(int_b_c_num)

int_exp_c_num<- as.numeric(unlist(int_exp_c))
mean_int_exp_c<-mean(int_exp_c_num)

int_act_c_num<- as.numeric(unlist(int_act_c))
mean_int_act_c<-mean(int_act_c_num)

#contrast between intercept C and E
int_b_con<-int_b[,grep("b_logboldness_treatmentE", colnames(int_b))]
int_exp_con<-int_b[,grep("b_exploration_treatmentE", colnames(int_b))]
int_act_con<-int_b[,grep("b_logactivity_treatmentE", colnames(int_b))]

#mean estimates for contrast
int_b_con_num<- as.numeric(unlist(int_b_con))
mean(int_b_con_num)

int_exp_con_num<- as.numeric(unlist(int_exp_con))
mean(int_exp_con_num)

int_act_con_num<- as.numeric(unlist(int_act_con))
mean(int_act_con_num)

#subtract intercept for C - contrast to get intercept for E
int_b_e<-(int_b_con_num + int_b_c_num)
mean_int_b_e<-mean(int_b_e)

int_exp_e<-(int_exp_con_num + int_exp_c_num)
mean_int_exp_e<-mean(int_exp_e)

int_act_e<-(int_act_con_num + int_act_c_num)
mean_int_act_e<-mean(int_act_e)

#95% IC
#Boldness
  #Control
blb_b_c <- round(quantile(int_b_c_num, c(0.025, 0.975))[1], 3)
bub_b_c <- round(quantile(int_b_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
blb_b_e<- round(quantile(int_b_e, c(0.025, 0.975))[1], 3)
bub_b_e<- round(quantile(int_b_e, c(0.025, 0.975))[2], 3)

#Exploration
  #Control
blb_exp_c <- round(quantile(int_exp_c_num, c(0.025, 0.975))[1], 3)
bub_exp_c <- round(quantile(int_exp_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
blb_exp_e <- round(quantile(int_exp_e, c(0.025, 0.975))[1], 3)
bub_exp_e <- round(quantile(int_exp_e, c(0.025, 0.975))[2], 3)

#Activity
  #Control
blb_act_c <- round(quantile(int_act_c_num, c(0.025, 0.975))[1], 3)
bub_act_c <- round(quantile(int_act_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
blb_act_e <- round(quantile(int_act_e, c(0.025, 0.975))[1], 3)
bub_act_e <- round(quantile(int_act_e, c(0.025, 0.975))[2], 3)

#Create data frame
dat_model<-data.frame(
  trait=c("logboldness","logboldness","exploration","exploration","logactivity","logactivity"),
  treatment=c("uninfected","infected","uninfected","infected","uninfected","infected"), 
  estimate = c(mean_int_b_c,mean_int_b_e,mean_int_exp_c,mean_int_exp_e, mean_int_act_c, mean_int_act_e), 
  Lower_CI = c(blb_b_c, blb_b_e, blb_exp_c, blb_exp_e, blb_act_c, blb_act_e),
  Higher_CI = c(bub_b_c,bub_b_e,bub_exp_c,bub_exp_e,bub_act_c,bub_act_e))

#plot model2      

trt <- as.factor(all_data$treatment)

m1<-ggplot(all_data, aes(x = trt, y = log_boldness, group = trt)) +
geom_violin(aes(fill = trt), trim = FALSE) +
geom_jitter(shape=16, position=position_jitter(0.1), color = "grey") +
geom_errorbar(data = dat_model,aes(x = treatment,y = estimate, ymin= Lower_CI, ymax=Higher_CI, group = trait == "logboldness"), width=0.4, inherit.aes = FALSE)+
scale_fill_manual(breaks = c("23", "28"), 
                   values=c("#429ef5", "#f54242")) +
labs(x = "Treatment", 
y = "Log_boldness") +
theme_classic() +
theme(legend.position = "none",
 legend.title = element_blank()) +
geom_segment(aes(x = 1, xend = 2, y = 6.5, yend = 6.5)) +
annotate(geom = "text", label=TeX("$p_$ = "), x = 1.5, y = 6.7 )

#filter boldness data
#match the names
#differentes couleurs pour infecter et non infecté
#errorbar black
#transparent
#compare mean estimate for pmcmc
            #geom_errorbar (put manually estimate + CI)

dat <- data.frame(metab = (all_data$log_activity), trt)

m2<-ggplot(dat, aes(x = trt, y = metab, group = trt)) +
geom_violin(aes(fill = trt), trim = FALSE) +
geom_jitter(shape=16, position=position_jitter(0.1), color = "grey") +
scale_fill_manual(breaks = c("23", "28"), 
                   values=c("#429ef5", "#f54242")) +
labs(x = "Treatment", 
y = "Log_activity",) +
theme_classic() +
theme(legend.position = "none",
 legend.title = element_blank()) +
geom_segment(aes(x = 1, xend = 2, y = 6.5, yend = 6.5)) +
annotate(geom = "text", label="p < 0.001", x = 1.5, y = 6.7 )

dat <- data.frame(metab = (all_data$exploration), trt)

m3<-ggplot(dat, aes(x = trt, y = metab, group = trt)) +
geom_violin(aes(fill = trt), trim = FALSE) +
geom_jitter(shape=16, position=position_jitter(0.1), color = "grey") +
scale_fill_manual(breaks = c("23", "28"), 
                   values=c("#429ef5", "#f54242")) +
labs(x = "Treatment", 
y = "Exploration") +
theme_classic() +
theme(legend.position = "none",
 legend.title = element_blank()) +
geom_segment(aes(x = 1, xend = 2, y = 6.5, yend = 6.5)) +
annotate(geom = "text", label="p < 0.001", x = 1.5, y = 6.7 )

 plot_grid(
  m1,m2,m3,
  labels = "AUTO", ncol = 3)
 
#Extract post sd from model 2 for each traits and treatment
# AT ID LEVEL HERE
#post_sd_2 <- as_draws_df(model2, variable = "^sd", regex = TRUE)
#Control
#post_b_c<-post_sd_C_2[,grep("logboldness", colnames(post_sd_C_2))]
#post_exp_c<-post_sd_C_2[,grep("exploration", colnames(post_sd_C_2))]
#post_act_c<-post_sd_C_2[,grep("logactivity", colnames(post_sd_C_2))]

#Experimental
#post_b_e<-post_sd_E_2[,grep("logboldness", colnames(post_sd_E_2))]
#post_exp_e<-post_sd_E_2[,grep("exploration", colnames(post_sd_E_2))]
#post_act_e<-post_sd_E_2[,grep("logactivity", colnames(post_sd_E_2))]

#unlist the data to be able to use the data as numeric
#Control
#post_b_c_num<- as.numeric(unlist(post_b_c))
#post_exp_c_num<- as.numeric(unlist(post_exp_c))
#post_act_c_num<- as.numeric(unlist(post_act_c))

#Experimental
#post_b_e_num<- as.numeric(unlist(post_b_e))
#post_exp_e_num<- as.numeric(unlist(post_exp_e))
#post_act_e_num<- as.numeric(unlist(post_act_e))

#calculate mean estimate
#Control
#mean_b_c<-mean(post_b_c_num)
#mean_exp_c<-mean(post_exp_c_num)
#mean_act_c<-mean(post_act_c_num)

#Experimental
#mean_b_e<-mean(post_b_e_num)
#mean_exp_e<-mean(post_exp_e_num)
#mean_act_e<-mean(post_act_e_num)

#95% IC
#Boldness
  #Control
#blb_b_c <- round(quantile(post_b_c_num, c(0.025, 0.975))[1], 3)
#bub_b_c <- round(quantile(post_b_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
#blb_b_e<- round(quantile(post_b_e_num, c(0.025, 0.975))[1], 3)
#bub_b_e<- round(quantile(post_b_e_num, c(0.025, 0.975))[2], 3)

#Exploration
  #Control
#blb_exp_c <- round(quantile(post_exp_c_num, c(0.025, 0.975))[1], 3)
#bub_exp_c <- round(quantile(post_exp_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
#blb_exp_e <- round(quantile(post_exp_e_num, c(0.025, 0.975))[1], 3)
#bub_exp_e <- round(quantile(post_exp_e_num, c(0.025, 0.975))[2], 3)

#Activity
  #Control
#blb_act_c <- round(quantile(post_act_c_num, c(0.025, 0.975))[1], 3)
#bub_act_c <- round(quantile(post_act_c_num, c(0.025, 0.975))[2], 3)
  #Experimental
#blb_act_e <- round(quantile(post_act_e_num, c(0.025, 0.975))[1], 3)
#bub_act_e <- round(quantile(post_act_e_num, c(0.025, 0.975))[2], 3)

#create data frame with metrics from posterior distribution from model2
#dat_model2<-data.frame(
  #trait=c("logboldness","logboldness","exploration","exploration","logactivity","logactivity"),
  #treatment=c("uninfected","infected","uninfected","infected","uninfected","infected"), 
  #estimate = c(mean_b_c,mean_b_e,mean_exp_c,mean_exp_e, mean_act_c,mean_act_e), 
  #Lower_CI = c(blb_b_c, blb_b_e, blb_exp_c, blb_exp_e, blb_act_c, blb_act_e),
 # Higher_CI = c(bub_b_c,bub_b_e,bub_exp_c,bub_exp_e,bub_act_c,bub_act_e))

      
#plot model2      
#w1<-ggplot(data = dat_model2) +
#geom_point(mapping = aes(x = treatment, y = estimate, color = trait))
  
#w2<-ggplot(data = all_data) + 
#geom_point(mapping = aes(x = treatment, y = log_activity))

#w3<-ggplot(data = all_data) + 
#geom_point(mapping = aes(x = treatment, y = exploration))

 #plot_grid(
  #w1, w2, w3,
  #labels = "AUTO", ncol = 1)

```

```{r}
#| label: tbl-tab1
#| tbl-cap: Repeatbility estimates for traits
#| 
tab1 <- data.frame(Trait = c("Boldness (log)", "Exploration","Activity (log)"), 
                "Group C" = c(mean(R_C_boldness[,1]), mean(R_C_exploration[,1]), mean(R_C_activity[,1])), 
                  "2.5% CI (C)" = c((R_Blb_bold_C),(R_Blb_exp_C), (R_Blb_act_C)),
              "97.5% CI (C)" = c((R_Bub_bold_C), (R_Bub_exp_C),(R_Bub_act_C)),
                "Group E" = c(mean(R_E_boldness[,1]), mean(R_E_exploration[,1]), mean(R_E_activity[,1])),
              "2.5% CI (E)" = c((R_Blb_bold_E), (R_Blb_exp_E), (R_Blb_act_E)), "97.5% CI (E)" = c((R_Bub_bold_E), (R_Bub_exp_E), (R_Bub_act_E)), check.names = FALSE)

gt(tab1) 

```
